---
title: "Name harmonization"
author: "Willem Goossens"
date: "2026-09-10"
output: html_document
---

# START
Empty environment
```{r}
rm(list=ls())
```

Load packages
```{r}
library(tidyverse)
library(xml2)
library(plantnet)
library(rgbif)
library(taxize)
```

Load data
```{r}
# Original dataset
pol <- read.csv("../Data/Observation/observation_org_bees.csv")
nat <- read_csv("../Results/iNaturalist_bees_all.csv", show_col_types = FALSE)

# Identifications
pol_plantnet <- read.csv("../Results/Plantnet_identification.csv")
pol_plantnet_iNat <- read.csv("../Results/Plantnet_identification_iNat_all.csv")
```


Combine identifications
```{r}
# Make character
pol_plantnet$ID <- as.character(pol_plantnet$ID)
pol_plantnet <- bind_rows(pol_plantnet, pol_plantnet_iNat)
```


Combine observations
```{r}
## OBSERVATION.ORG ##
# Reduce dataset with relevant columns
pol_data <- pol |> dplyr::select(id, date, time, lat, lng, accuracy, euromed_region, validation.status,
                                 scientific.name, family, species.type, number, sex, life.stage, activity,
                                 related.species, link)

# Add source platform
pol_data$source <- "Observation.org"
pol_data <- pol_data |> relocate(source, .before = id)

# Change names for now
colnames(pol_data) <- c("Platform","Obs_ID","Date","Time","Latitude","Longitude","Coordinate_uncertainty","Euro+Med_region","Observation_quality",
                        "Pol_original","Pol_family_original","Pol_rank_original","Number","Sex","Life_stage","Activity",
                        "User_original","Link")

# Change ID
pol_data$Obs_ID <- as.character(pol_data$Obs_ID)


## iNATURALIST ##
# Assign the link
nat$link <- paste("https://www.inaturalist.org/observations/", nat$observation_uuid, sep= "")

# Get relevant columns
nat_data <- nat |> dplyr::select(observation_uuid, observed_on,  latitude, longitude,positional_accuracy, Country, quality_grade, anomaly_score, 
                                 name, family_inat, link)

# Assign source
nat_data$source <- "iNaturalist.org"
nat_data <- nat_data |> relocate(source, .before = observation_uuid)

colnames(nat_data) <- c("Platform","Obs_ID","Date", "Latitude","Longitude","Coordinate_uncertainty","Euro+Med_region","Observation_quality", "Anomaly_score",
                        "Pol_original","Pol_original_family", "Link")


## COMBINE ##
# Make sure date corresponds
pol_data$Date <- as.Date(pol_data$Date, format = "%Y-%m-%d")
nat_data$Date <- as.Date(nat_data$Date, format = "%Y-%m-%d")

# Combine
all_data <- bind_rows(pol_data, nat_data)
```


# BEE
## 2.1 GBIF
```{r}
# Get bee names
names <- all_data |> distinct(Pol_original, Pol_family_original, Pol_rank_original)
names$old_name <- names$Pol_original
names$Pol_original <- gsub(" spec.", "", names$Pol_original)
names$Pol_original <- gsub("-gr.", "", names$Pol_original)
names$Pol_original <- sub(".*\\((.*)\\).*", "\\1", names$Pol_original)
names$Pol_original <- gsub(" indet.", "", names$Pol_original)

# Check again with gbif
gbif <- name_backbone_checklist(names$Pol_original[1], kingdom = "ANIMALIA")
# Subdivide to avoid R crashing
for(i in 1: 10){
  # boundaries
  begin <- 1+ floor(length(names$Pol_original)/10*(i-1))
  end <- floor(length(names$Pol_original)/10 * i)
  # run 
  data_gbif <- name_backbone_checklist(names$Pol_original[begin: end], kingdom = "ANIMALIA")
  gbif <- bind_rows(gbif, data_gbif)
}
gbif <- gbif[-1,]

# Save because it takes some time
gbif_pol_all <- gbif


##########
# Get final names (i.e. when there are subspecies or species)
# Subspecies
gbif$final <- gbif$subspecies
gbif$final[is.na(gbif$final)] <- gbif$variety[is.na(gbif$final)]
gbif$final_key <- gbif$subspeciesKey
gbif$final_key[is.na(gbif$final_key)] <- gbif$varietyKey[is.na(gbif$final_key)]


##########
# Validated initial name
gbif_acc <-  gbif[gbif$status== "ACCEPTED" & gbif$matchType == "EXACT" ,]
# Subset
names_subset <- names[names$Pol_original %in% gbif_acc$verbatim_name, ]
# Add subspecies
names_subset$subspecies <- gbif_acc$final[match(names_subset$Pol_original, gbif_acc$verbatim_name)]
names_subset$rank[!is.na(names_subset$subspecies)] <- "Subspecies"
names_subset$key[!is.na(names_subset$subspecies)] <- gbif_acc$final_key[match(names_subset$Pol_original[!is.na(names_subset$subspecies)], gbif_acc$verbatim_name)]
# Species
names_subset$species <- gbif_acc$species[match(names_subset$Pol_original, gbif_acc$verbatim_name)]
names_subset$key[is.na(names_subset$rank) & !is.na(names_subset$species)] <- 
  gbif_acc$speciesKey[match(names_subset$Pol_original[is.na(names_subset$rank) & !is.na(names_subset$species)], gbif_acc$verbatim_name)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$species)] <- "Species"
# Genus
names_subset$genus <- gbif_acc$genus[match(names_subset$Pol_original, gbif_acc$verbatim_name)]
names_subset$key[is.na(names_subset$rank) & !is.na(names_subset$genus)] <- 
  gbif_acc$genusKey[match(names_subset$Pol_original[is.na(names_subset$rank) & !is.na(names_subset$genus)], gbif_acc$verbatim_name)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$genus)] <- "Genus"
# Family
names_subset$family <- gbif_acc$family[match(names_subset$Pol_original, gbif_acc$verbatim_name)]
names_subset$key[is.na(names_subset$rank) & !is.na(names_subset$family)] <- 
  gbif_acc$familyKey[match(names_subset$Pol_original[is.na(names_subset$rank) & !is.na(names_subset$family)], gbif_acc$verbatim_name)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$family)] <- "Family"
# Overall
names_subset$bee_name <- gbif_acc$canonicalName[match(names_subset$Pol_original, gbif_acc$verbatim_name)]
names_subset$bee_name_scientific <- gbif_acc$scientificName[match(names_subset$Pol_original, gbif_acc$verbatim_name)]

# Add to names overall
names$subspecies <- NA
names$rank <- NA
names$key <- NA
names$species <- NA
names$genus <- NA
names$family <- NA
names$bee_name <- NA
names$bee_name_scientific <- NA
names[names$Pol_original %in% gbif_acc$verbatim_name, ] <- names_subset




##########
# Higherrank 
# Check dataframe ourselves quickly
acc_gbif <- gbif[gbif$status== "ACCEPTED" & gbif$matchType == "HIGHERRANK" & gbif$rank == "SPECIES",]

# Subset
names_subset <- names[names$Pol_original %in% acc_gbif$verbatim_name, ]
# Remove some that you want to keep
acc_gbif <- acc_gbif[!acc_gbif$verbatim_name %in% c( "Amegilla quadrifasciata maderae"),]
names_subset <- names_subset[!names_subset$Pol_original %in% c( "Amegilla quadrifasciata maderae"),]

# Species
names_subset$species <- acc_gbif$species[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$species)] <- "Species"
names_subset$key <- acc_gbif$speciesKey[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# Genus
names_subset$genus <- acc_gbif$genus[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# Family
names_subset$family <- acc_gbif$family[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# Canonical name
names_subset$bee_name <- acc_gbif$canonicalName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$bee_name_scientific <- acc_gbif$scientificName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]

# Add
names[names$Pol_original %in% acc_gbif$verbatim_name, ] <- names_subset




##########
# Synonyms
# Check dataframe ourselves quickly
acc_gbif <- gbif[gbif$status== "SYNONYM" & gbif$matchType %in% c("EXACT", "HIGHERRANK"),]

# Subset
names_subset <- names[names$Pol_original %in% acc_gbif$verbatim_name, ]

# Add subspecies
names_subset$subspecies <- acc_gbif$final[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$rank[!is.na(names_subset$subspecies)] <- "Subspecies"
names_subset$key <- acc_gbif$final_key[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# Species
names_subset$species <- acc_gbif$species[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$key[is.na(names_subset$rank) & !is.na(names_subset$species)] <- 
  acc_gbif$speciesKey[match(names_subset$Pol_original[is.na(names_subset$rank) & !is.na(names_subset$species)], acc_gbif$verbatim_name)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$species)] <- "Species"
# These are all subgenera, we add genus as is
names_subset$genus <- acc_gbif$genus[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$key[is.na(names_subset$rank) & !is.na(names_subset$genus)] <- 
  acc_gbif$genusKey[match(names_subset$Pol_original[is.na(names_subset$rank) & !is.na(names_subset$genus)], acc_gbif$verbatim_name)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$genus)] <- "Subgenus"
# Family
names_subset$family <- acc_gbif$family[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# These will include the accepted name to the highest level
names_subset$bee_name <- name_parse(acc_gbif$acceptedScientificName[match(names_subset$Pol_original, acc_gbif$verbatim_name)])$canonicalname
names_subset$bee_name_scientific <- acc_gbif$acceptedScientificName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$bee_name[names_subset$rank %in% "Subgenus"] <- acc_gbif$canonicalName[match(names_subset$Pol_original[names_subset$rank %in% "Subgenus"], acc_gbif$verbatim_name)]
names_subset$bee_name_scientific[names_subset$rank %in% "Subgenus"] <-
  acc_gbif$scientificName[match(names_subset$Pol_original[names_subset$rank %in% "Subgenus"], acc_gbif$verbatim_name)]


# Add
names[names$Pol_original %in% acc_gbif$verbatim_name, ] <- names_subset




##########
# REMAINING
gbif_remaining <- gbif[!gbif$verbatim_name %in% names$Pol_original[!is.na(names$key)],]
acc_gbif <- gbif_remaining[gbif_remaining$status== "ACCEPTED" & gbif_remaining$matchType == "HIGHERRANK" & gbif_remaining$rank == "GENUS",]

# Remove some
acc_gbif <- acc_gbif[!acc_gbif$verbatim_name %in% c("Lasioglossum haesitans", "Lasioglossum fulvicorne-fratellum", "Eucera subtilis","Eucera rhodia",
                                                   "Eucera multesima" ,"Eucera major", "Andrena taedium", "Megachile strymonia", "Bombus konradini") ,]

# Subset
names_subset <- names[names$Pol_original %in% acc_gbif$verbatim_name, ]

# Genus
names_subset$genus <- acc_gbif$genus[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$genus)] <- "Genus"
names_subset$key <- acc_gbif$genusKey[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# Family
names_subset$family <- acc_gbif$family[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# These will include the accepted name to the highest level
names_subset$bee_name <- acc_gbif$canonicalName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$rank[grepl(".*\\((.*)\\).*", names_subset$old_name)] <- "Subgenus"
names_subset$bee_name_scientific <- acc_gbif$scientificName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]

# Add
names[names$Pol_original %in% acc_gbif$verbatim_name, ] <- names_subset




##########
# REMAINING
gbif_remaining <- gbif[!gbif$verbatim_name %in% names$Pol_original[!is.na(names$key)],]
acc_gbif <- gbif_remaining[gbif_remaining$status %in% "PROVISIONALLY_ACCEPTED" ,]

# Remove some
acc_gbif <- acc_gbif[!acc_gbif$verbatim_name %in% c("Nomiapis monstrosa") ,]

# These are all subgenera
subgenus_to_genus <- tibble(subgenus = acc_gbif$genus ) |>
  mutate(genus = case_when(
    str_detect(subgenus, regex("andrena"))   ~ "Andrena",
    str_detect(subgenus, regex("halictus"))  ~ "Halictus",
    str_detect(subgenus, regex("bombus"))    ~ "Bombus",
    str_detect(subgenus, regex("megachile")) ~ "Megachile",
    str_detect(subgenus, regex("anthidium")) ~ "Anthidium",
    str_detect(subgenus, regex("xylocopa"))  ~ "Xylocopa",
    str_detect(subgenus, regex("ceratina"))  ~ "Ceratina",
    str_detect(subgenus, regex("osmia"))     ~ "Osmia",
    str_detect(subgenus, regex("coelioxys")) ~ "Coelioxys",
    str_detect(subgenus, regex("amegilla"))   ~ "Amegilla",
    str_detect(subgenus, regex("apis"))      ~ "Apis",
    str_detect(subgenus, regex("eucera"))    ~ "Eucera",
    str_detect(subgenus, regex("anthophora"))    ~ "Anthophora",
    # Manual assignments
    subgenus == "Sphecodogastra"      ~ "Lasioglossum",   
    subgenus == "Chalicodoma"         ~ "Megachile",
    subgenus == "Copoxyla"            ~ "Xylocopa",
    subgenus == "Eutricharaea"        ~ "Megachile",
    subgenus == "Anodonteutricharaea" ~ "Megachile",
    subgenus == "Xanthosarus"         ~ "Megachile",
    subgenus == "Bombias"             ~ "Bombus",
    subgenus == "Hexataenites"        ~ "Halictus",
    subgenus == "Lambdopsis"          ~ "Hylaeus",
    subgenus == "Dentigera"           ~ "Hylaeus",
    subgenus == "Paraprosopis"        ~ "Hylaeus",
    subgenus == "Spatulariella"       ~ "Hylaeus",
    subgenus == "Anthocopa"           ~ "Hoplitis",
    subgenus == "Alcidamea"           ~ "Hoplitis",
    subgenus == "Petalosternon"       ~ "Anthophora",
    subgenus == "Koptortosoma"        ~ "Xylocopa",
    subgenus == "Lophanthophora"      ~ "Anthophora",
    subgenus == "Pyganthophora"       ~ "Anthophora",
    subgenus == "Melanapis"           ~ "Andrena",
    subgenus == "Pseudapis"           ~ "Pseudapis",  
    TRUE ~ NA_character_ ))

# Subset
names_subset <- names[names$Pol_original %in% acc_gbif$verbatim_name, ]

# Genus
names_subset$genus <- subgenus_to_genus$genus[match(names_subset$Pol_original, subgenus_to_genus$subgenus)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$genus)] <- "Subgenus"
names_subset$key <- acc_gbif$genusKey[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# These will include the accepted name to the highest level
names_subset$bee_name <- acc_gbif$canonicalName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$rank[grepl(".*\\((.*)\\).*", names_subset$old_name)] <- "Subgenus"
names_subset$bee_name_scientific <- acc_gbif$scientificName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]

# Assign family
fam <- data.frame(genus =unique(names_subset$genus),
                  family =c("Halictidae","Andrenidae", "Halictidae", "Apidae","Megachilidae", "Apidae", "Megachilidae", "Apidae", "Apidae", "Apidae","Apidae",    
                            "Megachilidae", "Megachilidae", "Colletidae", "Apidae", "Megachilidae"))

names_subset$family <- fam$family[match(names_subset$genus, fam$genus)]

# Add
names[names$Pol_original %in% acc_gbif$verbatim_name, ] <- names_subset




##########
# REMAINING
gbif_remaining <- gbif[!gbif$verbatim_name %in% names$Pol_original[!is.na(names$key)],]
acc_gbif <- gbif_remaining[gbif_remaining$matchType %in% "VARIANT" ,]

# Subset
names_subset <- names[names$Pol_original %in% acc_gbif$verbatim_name, ]

# Add subspecies
names_subset$subspecies <- acc_gbif$final[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$rank[!is.na(names_subset$subspecies)] <- "Subspecies"
names_subset$key <- acc_gbif$final_key[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# Species
names_subset$species <- acc_gbif$species[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$key[is.na(names_subset$rank) & !is.na(names_subset$species)] <- 
  acc_gbif$speciesKey[match(names_subset$Pol_original[is.na(names_subset$rank) & !is.na(names_subset$species)], acc_gbif$verbatim_name)]
names_subset$rank[is.na(names_subset$rank) & !is.na(names_subset$species)] <- "Species"
# Genus
names_subset$genus <- acc_gbif$genus[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# Family
names_subset$family <- acc_gbif$family[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
# Canonical name
names_subset$bee_name <- acc_gbif$canonicalName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]
names_subset$bee_name_scientific <- acc_gbif$scientificName[match(names_subset$Pol_original, acc_gbif$verbatim_name)]

# Add
names[names$Pol_original %in% acc_gbif$verbatim_name, ] <- names_subset



##########
# TRIBES and SUBFAMILY
# Subset
names_subset <- names[(grepl("ni$", names$Pol_original) | grepl("nae$", names$Pol_original)) & is.na(names$key),] 
names_subset <- names_subset[!names_subset$Pol_original %in% c("Bombus konradini"),]  

# Assign the ranks
names_subset$rank[grepl("ni$", names_subset$Pol_original)] <- "Tribe"
names_subset$rank[grepl("nae$", names_subset$Pol_original)] <- "Subfamily"

# Assign bee name
names_subset$bee_name <- names_subset$Pol_original

taxonomy <- data.frame( group = c("Rophitinae","Apinae","Megachilinae","Melectini",
    "Andreninae","Nomadini","Lithurginae","Xylocopini",
    "Nomioidinae","Bombini","Nomiinae","Xylocopinae",
    "Epeolini","Hylaeinae","Colletinae","Andrenini",
    "Melittinae","Dioxyini","Dasypodaini","Ammobatini",
    "Euglossini", "Anthidiini", "Anthophorini","Eucerini","Halictinae",
    "Halictini","Megachilini","Nomadinae","Osmiini","Panurginae","Panurgini", "Eucerinae",
    "Nomioidini", "Meliponini","Anthophorinae "),
  family = c("Halictidae","Apidae","Megachilidae","Apidae",
    "Andrenidae","Apidae","Megachilidae","Apidae",
    "Halictidae","Apidae","Halictidae","Apidae",
    "Apidae","Colletidae","Colletidae","Andrenidae",
    "Melittidae","Megachilidae","Melittidae","Apidae",
    "Apidae", "Megachilidae", "Apidae","Apidae", "Halictidae",
    "Halictidae", "Megachilidae", "Apidae", "Megachilidae", "Andrenidae","Andrenidae", "Apidae",
    "Halictidae","Apidae","Apidae"))

# Assign
names_subset$family <- taxonomy$family[match(names_subset$Pol_original, taxonomy$group)]

# Add
names[names$Pol_original %in% names_subset$Pol_original ,] <- names_subset




##########
# REMAINING
names_subset <- names[is.na(names$bee_name), ]
gbif_remaining <- gbif[!gbif$verbatim_name %in% names$Pol_original[!is.na(names$bee_name)] ,]

# Some data is already assigned at the genus level
names_data <- names[!is.na(names$bee_name),]
names_subset <- names_subset[names_subset$Pol_original %in% names_data$genus,]

names_subset$genus <- names_data$genus[match(names_subset$Pol_original, names_data$genus)]
names_subset$family <- names_data$family[match(names_subset$Pol_original, names_data$genus)]
names_subset$rank <- "Genus"
names_subset$bee_name <- names_data$genus[match(names_subset$Pol_original, names_data$genus)]

# Add
names[names$Pol_original %in% names_subset$Pol_original ,] <- names_subset





##########
# REMAINING
names_subset <- names[is.na(names$bee_name), ]
gbif_remaining <- gbif[!gbif$verbatim_name %in% names$Pol_original[!is.na(names$bee_name)] ,]

# Assign some extra
taxonomy_lookup <- data.frame(
  taxon = c("Prosopis","Chlorandrena","Pteneucera", "Paracoelioxys","Panurgina","Rozeniana","Panurginina","Apidae", "Collicula",
            "Eupavlovskia","Heliophila", "Nomiapis", "Acrosmia", "Trigona"),
  genus = c(  "Hylaeus", "Andrena","Eucera", "Coelioxys", NA,"Coelioxys",NA, NA,
              "Nomada", "Eupavlovskia","Anthophora", "Pseudapis", "Hoplitis",
              "Trigona"),
  family = c( "Colletidae","Andrenidae","Apidae", "Megachilidae", "Andrenidae",  "Megachilidae","Andrenidae", "Apidae", "Apidae","Apidae","Apidae", "Halictidae",
              "Megachilidae", "Apidae"),
  rank = c(  "Subgenus", "Subgenus", "Subgenus", "Subgenus", "Subtribe", "Subgenus","Subtribe", "Family", "Subgenus", "Genus", "Subgenus", "Genus",
             "Subgenus", "Genus"))

# Assign
names_subset$genus <- taxonomy_lookup$genus[match(names_subset$Pol_original, taxonomy_lookup$taxon)]
names_subset$family <- taxonomy_lookup$family[match(names_subset$Pol_original, taxonomy_lookup$taxon)]
names_subset$rank <- taxonomy_lookup$rank[match(names_subset$Pol_original, taxonomy_lookup$taxon)]
names_subset$bee_name <- taxonomy_lookup$taxon[match(names_subset$Pol_original, taxonomy_lookup$taxon)]

# Add
names[is.na(names$bee_name), ] <- names_subset



##########
# REMAINING
names_subset <- names[is.na(names$bee_name), ]
names_subset$species <- names_subset$Pol_original

# Change some
names_subset$species[names_subset$Pol_original %in% c("Amegilla quadrifasciata maderae")] <- "Stelis ornatula"
names_subset$species[names_subset$Pol_original %in% c("Nomiapis monstrosa")] <- "Pseudapis monstrosa"
# Get genus
names_subset$genus <- vegdata::parse.taxa(names_subset$species)[[2]]
# Get family
names_data <- names[!is.na(names$bee_name),]
fam <- names_data |> distinct(genus, family)
names_subset$family <- fam$family[match(names_subset$genus, fam$genus)]
# Assign rank
names_subset$rank <- "Species"
names_subset$rank[names_subset$Pol_original %in% c("Lasioglossum fulvicorne-fratellum")] <- "Aggregate"
names_subset$bee_name <- names_subset$species

# Add
names[is.na(names$bee_name), ] <- names_subset

# Save version before changes
names_save <- names
```


## 2.2 Changes
```{r}
# Change aggregates
names$rank[grepl("/", names$old_name)] <- "Aggregate"
names$rank[grepl("-gr.", names$old_name)] <- "Aggregate"

# We will save the complexes to the bee name but remove from the species column
# We than have to remove the key and scientific name as well
names$species[grepl("/", names$old_name)] <-  NA
names$species[names$old_name %in% "Lasioglossum fulvicorne-fratellum"] <-  NA
names$bee_name[grepl("/", names$old_name)] <- names$old_name[grepl("/", names$old_name)]
names$bee_name[names$old_name %in% "Lasioglossum fulvicorne-fratellum"] <-  "Lasioglossum fratellum/subfulvicorne"
names$bee_name_scientific[grepl("/", names$old_name)] <- NA
names$key[grepl("/", names$old_name)] <- NA


# Look at whether there are differences in bee name and species
check <- names[!is.na(names$species),]
check <- check[check$species != check$bee_name,]

# This one is wrong in gbif, (a vs us), we will just keep the name here (then in corresponds at the species level)
names$subspecies[names$old_name %in% "Halictus subauratus corsa"] <- "Halictus subauratus corsa"
names$bee_name[names$old_name %in% "Halictus subauratus corsa"] <- "Halictus subauratus corsa"
names$bee_name_scientific[names$old_name %in% "Halictus subauratus corsa"] <- "Halictus subauratus corsa Blüthgen, 1933"
names$rank[names$old_name %in% "Halictus subauratus corsa"] <- "Subspecies"

# Fix some errors
names$subspecies[names$old_name %in% "Anthidium melanopygum"] <- "Anthidium spiniventre melanopygum"
names$species[names$old_name %in% "Anthidium melanopygum"] <- "Anthidium spiniventre"
names$species[names$old_name %in% "Anthidium melanopygum"] <- "Anthidium spiniventre"
names$rank[names$old_name %in% "Anthidium melanopygum"] <- "Subspecies"
names$bee_name[names$old_name %in% "Anthidium melanopygum"] <- "Anthidium spiniventre melanopygum"
names$bee_name_scientific[names$old_name %in% "Anthidium melanopygum"] <- "Anthidium spiniventre melanopygum Friese, 1917"
names$key[names$old_name %in% "Anthidium melanopygum"] <- NA

# Fix some errors
names$species[names$old_name %in% "Eucera terminata"] <- "Eucera terminata"
names$bee_name[names$old_name %in% "Eucera terminata"] <- "Eucera terminata"
names$bee_name_scientific[names$old_name %in% "Eucera terminata"] <- "Eucera terminata Pérez, 1895"
names$key[names$old_name %in% "Eucera terminata"] <- NA

# Fix other errors
names$subspecies[names$old_name %in% "Lasioglossum laticeps hellenicum"] <- "Lasioglossum laticeps hellenicum"
names$bee_name[names$old_name %in% "Lasioglossum laticeps hellenicum"] <- "Lasioglossum laticeps hellenicum"
names$bee_name_scientific[names$old_name %in% "Lasioglossum laticeps hellenicum"] <- "Lasioglossum laticeps hellenicum Blüthgen, 1937"
names$rank[names$old_name %in% "Lasioglossum laticeps hellenicum"] <- "Subspecies"
names$key[names$old_name %in% "Lasioglossum laticeps hellenicum"] <- NA

# Look at whether there are differences in bee name and species
check <- names[!is.na(names$genus),]
check <- check[check$genus != check$bee_name & check$rank %in% "Genus",]
names$bee_name[names$Pol_original %in% "Nomiapis"] <- "Pseudapis"

# Some other errors
# Seladonia
names$species[names$old_name %in% "Halictus submediterraneus"] <- "Halictus submediterraneus"
names$genus[names$old_name %in% "Halictus submediterraneus"] <- "Halictus"
names$rank[names$old_name %in% "Halictus submediterraneus"] <- "Species"
names$bee_name[names$old_name %in% "Halictus submediterraneus"] <- "Halictus submediterraneus"
names$bee_name_scientific[names$old_name %in% "Halictus submediterraneus"] <- "Halictus submediterraneus Pauly, 2015"
names$key[names$old_name %in% "Halictus submediterraneus"] <- NA
names$genus[names$Pol_original %in% "Seladonia"] <- "Halictus"
names$bee_name[names$Pol_original %in% "Seladonia"] <- "Halictus"
names$bee_name_scientific[names$Pol_original %in% "Seladonia"] <- "Halictus Latreille, 1804"
names$key[names$Pol_original %in% "Seladonia"] <- NA

# Megachile schmiedeknechti
names$species[names$old_name %in% "Megachile argentata schmiedeknechti"] <- "Megachile schmiedeknechti"
names$bee_name[names$old_name %in% "Megachile argentata schmiedeknechti"] <- "Megachile schmiedeknechti"
names$bee_name_scientific[names$old_name %in% "Megachile argentata schmiedeknechti"] <- "Megachile schmiedeknechti Costa, 1884"
names$key[names$old_name %in% "Megachile argentata schmiedeknechti"] <- NA
```


## 2.3 Check
```{r}
###### 
# Incorrect families
# Check for duplicated genera with different families
dup <- names |> distinct(genus, family)
dup <- dup[duplicated(dup$genus) | duplicated(dup$genus, fromLast = T),]
dup <- dup[order(dup$genus),]
names$family[names$genus %in% dup$genus[1]] <- "Halictidae"

# Check whether these are all bee families
dup <- names[!names$family %in% c("Apidae","Melittidae","Megachilidae","Colletidae","Halictidae","Andrenidae"),]
# Change a tribe
names$family[names$Pol_original %in% "Ceratinini"] <- "Apidae"
names$rank[names$Pol_original %in% "Ceratinini"] <- "Tribe"
names$bee_name_scientific[names$Pol_original %in% "Ceratinini"] <- NA
names$bee_name[names$Pol_original %in% "Ceratinini"] <- "Ceratinini"
# Change a subtribe
names$rank[names$Pol_original %in% "Halictina"] <- "Subtribe"
names$genus[names$Pol_original %in% "Halictina"] <- NA

# Remove some
remove <- c("Anthophila","Sphecodina")
names <- names[!names$old_name %in% remove, ]
all_data <- all_data[!all_data$Pol_original %in% remove,]
# Assign some extra
taxonomy_lookup <- data.frame(
  taxon = c("Mellitoides","Anthophorinae","Leucandrena", "Panurgina"),
  genus = c("Andrena",NA,"Andrena",  NA),
  family = c("Andrenidae","Apidae" , "Andrenidae", "Andrenidae"),
  rank = c("Subgenus", "Subfamily","Subgenus", "Subtribe"))

# Assign
names$genus[names$Pol_original %in% dup$Pol_original] <- taxonomy_lookup$genus[match(names$Pol_original[names$Pol_original %in% dup$Pol_original], taxonomy_lookup$taxon)]
names$family[names$Pol_original %in% dup$Pol_original] <- taxonomy_lookup$family[match(names$Pol_original[names$Pol_original %in% dup$Pol_original], taxonomy_lookup$taxon)]
names$rank[names$Pol_original %in% dup$Pol_original] <- taxonomy_lookup$rank[match(names$Pol_original[names$Pol_original %in% dup$Pol_original], taxonomy_lookup$taxon)]
names$bee_name[names$Pol_original %in% dup$Pol_original] <- taxonomy_lookup$taxon[match(names$Pol_original[names$Pol_original %in% dup$Pol_original], taxonomy_lookup$taxon)]
names$key[names$Pol_original %in% dup$Pol_original] <- NA



###### 
# Unidentified ranks
dup <- names[is.na(names$Pollinator_rank),]



###### 
# Incorrect species
dup <- names |> distinct(species, genus, family)
dup <- dup[duplicated(dup$species) | duplicated(dup$species, fromLast = T),]
dup <- dup[order(dup$species) & !is.na(dup$species),]




###### 
# Incorrect subspecies
dup <- names |> distinct(subspecies, species, genus, family)
dup <- dup[duplicated(dup$subspecies) | duplicated(dup$subspecies, fromLast = T),]
dup <- dup[!is.na(dup$subspecies),]
# None are found to be incorrect




###### 
# Incorrect ranks
dup <- names |> distinct(bee_name,  species, genus, family)
dup <- dup[duplicated(dup$bee_name) | duplicated(dup$bee_name, fromLast = T),]
dup <- dup[order(dup$bee_name),]


###### 
# Check one last time 
dup <- names |> distinct(bee_name,  species, genus, family, old_name)
dup <- dup[duplicated(dup$old_name) | duplicated(dup$old_name, fromLast = T),]
dup <- dup[order(dup$bee_name),]

# Change a tribe again (keeps giving errors)
names$family[names$Pol_original %in% "Ceratinini"] <- "Apidae"
names$rank[names$Pol_original %in% "Ceratinini"] <- "Tribe"
names$bee_name_scientific[names$Pol_original %in% "Ceratinini"] <- NA
names$bee_name[names$Pol_original %in% "Ceratinini"] <- "Ceratinini"


names_save <- names

###### 
# get unique dataframe
bee_names <-  names_save |> distinct(bee_name, bee_name_scientific, key, rank, subspecies, species, genus, family, old_name)
```


```{r}
########
# We will look whether we can assign new ID's or accepted names
non_acc <- bee_names[is.na(bee_names$bee_name_scientific),]
# Look for accepted names
acc <-  bee_names[!is.na(bee_names$bee_name_scientific),]

# Assign
non_acc$bee_name_scientific <- acc$bee_name_scientific[match(non_acc$bee_name, acc$bee_name)]
non_acc$key <- acc$key[match(non_acc$bee_name, acc$bee_name)]

# Assign
non_acc$key <- as.integer(as.character(non_acc$key))
bee_names[is.na(bee_names$bee_name_scientific),] <- non_acc


# Assign also keys for genera etc
non_acc <- bee_names[is.na(bee_names$bee_name_scientific) & !bee_names$rank %in% c("Aggregate"),]
gbif <-  name_backbone_checklist(non_acc$bee_name[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(non_acc$bee_name)/2*(i-1))
  end <- floor(length(non_acc$bee_name)/2 * i)
  # run 
  data <- name_backbone_checklist(non_acc$bee_name[begin: end])
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]

# We can add one more
gbif_acc <- gbif[gbif$matchType %in% "EXACT" & gbif$kingdom %in% "Animalia",]
bee_names$key[is.na(bee_names$key)] <- gbif_acc$usageKey[match(bee_names$bee_name[is.na(bee_names$key)], gbif_acc$verbatim_name)]
bee_names$bee_name_scientific[is.na(bee_names$key)] <- gbif_acc$scientificName[match(bee_names$bee_name[is.na(bee_names$key)], gbif_acc$verbatim_name)]


gbif <- data.frame()
######
# Get the remaining GBIF ID's
# Maybe better to also remove subfamilies and tribes, the function does not get these
non_acc <- bee_names[is.na(bee_names$bee_name_scientific) & !bee_names$rank %in% c("Aggregate", "Tribe","Subtribe","Subfamily", "Subgenus"),]
non_acc <- non_acc[!duplicated(non_acc$bee_name),]
gbif <-  data.frame(name = non_acc$bee_name[1], gbif = get_gbifid(non_acc$bee_name[1])[[1]])
for(i in 1: nrow(non_acc)){
  # run 
  data <- data.frame(name = non_acc$bee_name[i], gbif = get_gbifid(non_acc$bee_name[i])[[1]])
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]
gbif_ids <- gbif

# Here we manually have to assign some, numbers are 2 1 2 1 1 NA NA 2 NA 2 NA NA 2 
non_acc$key <- gbif$gbif[match(non_acc$bee_name ,gbif$name,)]
non_acc$bee_name_new <- NA

# Check the species in gbif
for(i in 1: nrow(non_acc)){
  # run 
  if(is.na(non_acc$key[i])) next
  acc <- name_usage( key = non_acc$key[i])
  non_acc$bee_name_scientific[i] <- acc$data$scientificName
  non_acc$bee_name_new[i] <- acc$data$canonicalName
}

# Remove the uncertain ones
non_acc$bee_name_scientific[is.na(non_acc$key)] <- NA
uncertain <- non_acc[non_acc$bee_name != non_acc$bee_name_new & !is.na(non_acc$bee_name_scientific),]
uncertain <- uncertain[!uncertain$bee_name %in% "Lasioglossum laticeps hellenicum",]
non_acc$bee_name_scientific[non_acc$bee_name %in% uncertain$bee_name] <- NA
non_acc$key[non_acc$bee_name %in% uncertain$bee_name] <- NA
# How many are now assigned
sum(!is.na(non_acc$key))

# Remove one plant
non_acc$bee_name_scientific[non_acc$bee_name %in% "Heliophila"] <- "Heliophila Klug, 1807"
non_acc$key[non_acc$bee_name %in% "Heliophila"] <- NA



# Assign also keys for genera etc
non_acc_assign <- bee_names[is.na(bee_names$bee_name_scientific) & !bee_names$rank %in% c("Aggregate"),]
non_acc_assign$bee_name_scientific <- non_acc$bee_name_scientific[match(non_acc_assign$bee_name, non_acc$bee_name)]
non_acc_assign$key <- non_acc$key[match(non_acc_assign$bee_name, non_acc$bee_name)]

# Assign
non_acc_assign$key <- as.integer(as.character(non_acc_assign$key))
bee_names[is.na(bee_names$bee_name_scientific)& !bee_names$rank %in% c("Aggregate") ,] <- non_acc_assign


####
#Tribe, subtribe and subfamily
bee_names$key[bee_names$rank %in% c("Tribe","Subtribe","Subfamily")] <- NA
bee_names$bee_name_scientific[bee_names$rank %in% c("Tribe","Subtribe","Subfamily")] <- NA
bee_names$genus[bee_names$rank %in% c("Tribe","Subtribe","Subfamily")] <- NA



### 
# Another change
bee_names$bee_name_scientific[bee_names$old_name %in% c("Bombus konradini")] <- "Bombus lapponicus konradini Reinig, 1965"
bee_names$subspecies[bee_names$old_name %in% c("Bombus konradini")] <- "Bombus lapponicus konradini"
bee_names$species[bee_names$old_name %in% c("Bombus konradini")] <- "Bombus lapponicus"
bee_names$bee_name[bee_names$old_name %in% c("Bombus konradini")] <- "Bombus lapponicus konradini"



####
# How many remain
non_acc <- bee_names[is.na(bee_names$bee_name_scientific) & !bee_names$rank %in% c("Aggregate", "Tribe","Subtribe","Subfamily", "Subgenus"),]

# Assign scientific names that are for some reason not found
change <- data.frame(bee_name = non_acc$bee_name[order(non_acc$rank)],
                     science = c("Eupavlovskia Popov, 1955", "Trigona (Ktinotrofia) Engel, 2021","Eupavlovskia Popov, 1955",
                                 "Eupavlovskia obscura (Friese, 1895)","Lasioglossum haesitans (Blüthgen, 1931)","Eucera terminata Pérez, 1895",NA, NA,
                                 "Eupavlovskia funeraria (Smith, 1854)",NA, NA, NA, "Andrena taedium Wood, 2023" ))

# Assign
bee_names$bee_name_scientific[bee_names$bee_name %in% change$bee_name] <- change$science[match(bee_names$bee_name[bee_names$bee_name %in% change$bee_name], change$bee_name)]

# How many keys and scientific names do we have
length(unique(bee_names$key))
length(unique(bee_names$bee_name_scientific))
length(unique(bee_names$bee_name))

# Save
write_csv(bee_names, "../Results/Bee_name_all_last_version.csv")
```






## 2.4 Save
```{r}
# Assign
all_data$Bee_accepted_name <- bee_names$bee_name[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_accepted_scientific_name <- bee_names$bee_name_scientific[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_subspecies <- bee_names$subspecies[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_species <- bee_names$species[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_genus <- bee_names$genus[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_family <- bee_names$family[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_GBIF_key <- bee_names$key[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_rank <- bee_names$rank[match(all_data$Pol_original, bee_names$old_name)]

#write_csv(all_data, "../Results/Bees_all_observations.csv")
```



# PLANTNET
## 3.1 Load data
```{r}
# Get those observation in current dataset
pol_plantnet <- pol_plantnet[pol_plantnet$ID %in% all_data$Obs_ID,]

# Get unique identifications
plantnet <- pol_plantnet |> group_by(Name, Genus, Family, GBIF_ID, POWO_ID, IUCN_ID) |> summarise(n =n(), rel = mean(Score, na.rm=T))
```


## 3.2 GBIF
```{r}
# Names save
names_plantnet <- plantnet
# Assign GBIF names based on data
for(i in 1: nrow(names_plantnet)){
  if(is.na(names_plantnet$GBIF_ID[i])) next

  # Get synonym data
  acc <- name_usage( key = names_plantnet$GBIF_ID[i])
  # Add name of accepted species
  names_plantnet$GBIF[i] <- acc$data$canonicalName
  names_plantnet$GBIF_genus[i] <- acc$data$genus
  names_plantnet$GBIF_family[i] <- acc$data$family
  names_plantnet$GBIF_rank[i] <- acc$data$rank
  names_plantnet$GBIF_kingdom[i] <- acc$data$kingdom
  names_plantnet$GBIF_Status[i] <- acc$data$taxonomicStatus
  names_plantnet$GBIF_species[i] <- acc$data$species
  names_plantnet$GBIF_accepted[i] <- acc$data$scientificName

  
  # Add subspecies or variety
  if ("subspecies" %in% names(acc$data)) {
    names_plantnet$GBIF_subspecies[i] <- acc$data$subspecies
    } else {
    NA_character_
    }
  if ("variety" %in% names(acc$data)) {
    names_plantnet$GBIF_subspecies[i] <- acc$data$variety
    } else {
    NA_character_
  }
}

# Save to be certain for later because it takes a long time
names_plantnet_saved <- names_plantnet
```


## 3.3 ASSIGN
### Accepted
```{r}
# Get the saved version again (in case we made errors previously)
names_plantnet <- names_plantnet_saved
# Create a validated column
names_plantnet$validated <- NA

########
# ACCEPTED
# Add all thise for which GBIF has accepted
names_plantnet$validated[names_plantnet$GBIF_Status %in% "ACCEPTED" & !is.na(names_plantnet$GBIF_ID)] <- T
# Remove data for which GBIF did not assign an accepted name
names_plantnet[is.na(names_plantnet$GBIF_ID), 9:15] <- NA

# 1157 species still have to be validated
sum(is.na(names_plantnet$validated))

# Assign 
names_plantnet$GBIF_subspecies <- NA
```

### Synonyms
```{r}
# Synonyms
syn <- names_plantnet[names_plantnet$GBIF_Status == "SYNONYM" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),]
sum(is.na(syn$validated))

# Check whether none are subspecies
gbif <-  name_backbone_checklist(syn$Name[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(syn$GBIF)/2*(i-1))
  end <- floor(length(syn$GBIF)/2 * i)
  # run 
  data <- name_backbone_checklist(syn$GBIF[begin: end])
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]

# Save
gbif_two <- gbif
gbif <- gbif_two

# Check overall name
gbif$final <- gbif$variety
gbif$final[is.na(gbif$final)] <- gbif$subspecies[is.na(gbif$final)]

# Assign scientific name
gbif$scientificName[!is.na(gbif$acceptedScientificName)] <- gbif$acceptedScientificName[!is.na(gbif$acceptedScientificName)]
gbif$usageKey[!is.na(gbif$acceptedUsageKey)] <- gbif$acceptedUsageKey[!is.na(gbif$acceptedUsageKey)]


# Assign
gbif_syn <- gbif[!is.na(gbif$status) & gbif$matchType %in% "EXACT",]
syn[, 10:18] <- NA
# Subspecies
syn$GBIF_subspecies <- gbif_syn$final[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_rank[!is.na(syn$GBIF_subspecies)] <- "SUBSPECIES"
syn$GBIF[!is.na(syn$GBIF_subspecies)] <- syn$GBIF_subspecies[!is.na(syn$GBIF_subspecies)] 
syn$GBIF_ID[!is.na(syn$GBIF_subspecies)] <- gbif_syn$usageKey[match(syn$Name[!is.na(syn$GBIF_subspecies)], gbif_syn$verbatim_name)]
syn$GBIF_accepted[!is.na(syn$GBIF_subspecies)] <- gbif_syn$scientificName[match(syn$Name[!is.na(syn$GBIF_subspecies)], gbif_syn$verbatim_name)]
syn$validated[!is.na(syn$GBIF_subspecies)] <- T

# Species
syn$GBIF_species <- gbif_syn$species[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_genus<- gbif_syn$genus[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_family <- gbif_syn$family[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_rank[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)] <- "SPECIES"
syn$GBIF[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$species[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$GBIF_ID[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$usageKey[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$GBIF_accepted[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$scientificName[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$validated[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)] <- T
syn$validated[is.na(syn$Genus)] <- NA



########
# Check some errors by looking at correspondance at name level
gbif$final[is.na(gbif$final)] <- gbif$species[is.na(gbif$final)]
syn_correct <- syn[syn$GBIF %in% gbif$final,]
# These should be correct and will be considered validated

# But species vary for some
check <- names_plantnet[names_plantnet$GBIF %in% syn_correct$GBIF & is.na(names_plantnet$validated),] 
check <- check[check$GBIF != check$GBIF_species,]
change <- data.frame(old = check$GBIF, new = check$GBIF_species)
# 41 have to be changed
# Check all species combinations, some are correct (keep), some have to be further changed
keep <- change[c(2,3,9,10,11,13, 18, 20, 24, 28, 34,40),]
other <- change[c(6, 17,19 ,21, 25,30,31:33,35,39),]
change <- change[-c(2,3,9,10,11,13, 18, 20, 24, 28, 40, 6, 17,19 ,21, 25,30,31:33,35,39),]


# Update the other
other$final <- c("Erigeron glabratus occidentalis","Eruca vesicaria sativa", "Francoa appendiculata sonchifolia",
                 "Harrisia fragrans aboriginum", "Aphyllon cooperi cooperi", "Pulicaria arabica hispanica", "Ficaria verna verna",
                 "Rosa canina biserrata", "Rosa canina biserrata", "Rumex pratensis pratensis", "Betonica officinalis officinalis")
syn$GBIF_subspecies[syn$GBIF %in% other$old] <- other$final[match(syn$GBIF[syn$GBIF %in% other$old], other$old)]
syn$GBIF_species[syn$GBIF %in% other$old] <- paste(vegdata::parse.taxa(other$final[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]],
                                                       vegdata::parse.taxa(other$final[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[3]])
syn$GBIF_genus[syn$GBIF %in% other$old] <- (vegdata::parse.taxa(other$final[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]])
syn$GBIF[syn$GBIF %in% other$old] <- syn$GBIF_subspecies[syn$GBIF %in% other$old]
syn$GBIF_subspecies[syn$GBIF_subspecies == syn$GBIF_species] <- NA
syn$GBIF_rank[syn$GBIF %in% other$final] <- "SUBSPECIES"
syn$GBIF_accepted[syn$GBIF %in% other$final] <- NA
syn$GBIF_ID[syn$GBIF %in% other$final] <- NA
syn$validated[syn$GBIF %in% other$final] <- T

# Change the last
syn$GBIF_species[syn$GBIF %in% change$old] <- change$new[match(syn$GBIF[syn$GBIF %in% change$old], change$old)]
syn$GBIF_genus[syn$GBIF %in% change$old] <- (vegdata::parse.taxa(change$new[match(syn$GBIF[syn$GBIF %in% change$old], change$old)])[[2]])
syn$GBIF_rank[syn$GBIF %in% change$old] <- "SPECIES"
syn$GBIF[syn$GBIF %in% change$old] <- change$new[match(syn$GBIF[syn$GBIF %in% change$old], change$old)]
syn$GBIF_accepted[syn$Name %in% change$old] <- NA
syn$GBIF_ID[syn$Name %in% change$old] <- NA
syn$validated[syn$Name %in% change$old] <- T


# How many remain
sum(is.na(syn$validated))
sum(is.na(syn$GBIF_ID))




########
# Some did not correspond at subspecies level
syn_incorrect <- syn[!syn$GBIF %in% gbif$final,]

# So removes the different species
gbif_incorrect <- gbif[!gbif$final %in% syn$GBIF,]

# Reduce dataset to change everything in for safety
check <- names_plantnet[names_plantnet$GBIF %in% syn_incorrect$GBIF & is.na(names_plantnet$validated),] 

# Add subspecies
gbif_subsp <- gbif_incorrect[!is.na(gbif_incorrect$variety) | ! is.na(gbif_incorrect$subspecies),]
syn$GBIF_subspecies[is.na(syn$validated)] <- gbif_subsp$final[match(syn$GBIF[is.na(syn$validated)], gbif_subsp$verbatim_name)]
syn$GBIF_ID[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)] <- gbif_subsp$usageKey[match(syn$GBIF[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)],
                                                                                            gbif_subsp$verbatim_name)]
syn$GBIF_species[!is.na(syn$GBIF_subspecies) & is.na(syn$validated)]<- paste(vegdata::parse.taxa(syn$GBIF_subspecies[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)])[[2]],
                                                                             vegdata::parse.taxa(syn$GBIF_subspecies[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)])[[3]])
syn$GBIF_genus[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)] <- paste(vegdata::parse.taxa(syn$GBIF_subspecies[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)])[[2]])
syn$GBIF[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)] <- syn$GBIF_subspecies[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)]
syn$GBIF_rank[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)] <- "SUBSPECIES"
syn$validated[!is.na(syn$GBIF_subspecies)& is.na(syn$validated)] <- T


# Look at species
gbif_incorrect <-  gbif[!gbif$final %in% syn$GBIF,]
gbif_species <- gbif_incorrect[gbif_incorrect$matchType %in% "EXACT",]
syn$GBIF_species[is.na(syn$validated)] <- gbif_species$final[match(syn$GBIF[is.na(syn$validated)], gbif_species$verbatim_name)]
syn$GBIF_ID[is.na(syn$validated)] <- gbif_species$usageKey[match(syn$GBIF[is.na(syn$validated)], gbif_species$verbatim_name)]
syn$GBIF_genus[!is.na(syn$GBIF_species)& is.na(syn$validated)] <- paste(vegdata::parse.taxa(syn$GBIF_species[!is.na(syn$GBIF_species)& is.na(syn$validated)])[[2]])
syn$GBIF[!is.na(syn$GBIF_species)& is.na(syn$validated)] <- syn$GBIF_species[!is.na(syn$GBIF_species)& is.na(syn$validated)]
syn$GBIF_rank[!is.na(syn$GBIF_species)& is.na(syn$validated)] <- "SPECIES"
syn$validated[!is.na(syn$GBIF_species)& is.na(syn$validated)] <- T


# How many remain
sum(is.na(syn$validated))


# Which remain
gbif_incorrect <-  gbif[gbif$verbatim_name %in% syn$Name[is.na(syn$validated)],]

# Assign
syn_empty <- syn[is.na(syn$validated),]
# Change
other <- data.frame(old = syn_empty$Name, GBIF = syn_empty$GBIF)

# Add
other$new_name <- c(NA, NA, "Alchemilla arvensis", "Lachemilla pinnata",
                     "Calamagrostis arenaria", "Mahonia japonica", 
                     "Centaurea triumfettii semidecurrens", 
                     "Tarenaya spinosa", NA, "Crataegus coccinea",
                     "Culcitium canescens", 
                     "Pardoglossum cheirifolium cheirifolium", NA, NA,
                     "Draba verna", NA, NA, NA, NA, 
                     "Cynanchum insipidum", NA,
                     "Xanthoselinum alsaticum alsaticum", NA, NA,
                     "Rosa canina biserrata", NA, NA, "Petrosedum sediforme",
                     "Sedum candolleanum", "Atocion armeria", NA, NA,
                     "Vaccinium corymbosum", NA, NA, "Festuca myuros")
other$new_name[is.na(other$new_name)] <- other$GBIF[is.na(other$new_name)]

# Assign
syn$GBIF_subspecies[syn$GBIF %in% other$old] <- other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)]
syn$GBIF_species[syn$GBIF %in% other$old] <- paste(vegdata::parse.taxa(other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]],
                                                       vegdata::parse.taxa(other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[3]])
syn$GBIF_genus[syn$GBIF %in% other$old] <- (vegdata::parse.taxa(other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]])
syn$GBIF[syn$GBIF %in% other$old] <- syn$GBIF_subspecies[syn$GBIF %in% other$old]
syn$GBIF_subspecies[syn$GBIF_subspecies == syn$GBIF_species ] <- NA
syn$GBIF_rank[!is.na(syn$GBIF_subspecies)] <- "SUBSPECIES"
syn$GBIF_accepted[syn$Name %in% other$old] <- NA
syn$GBIF_ID[syn$Name %in% other$old] <- NA
syn$validated[syn$Name %in% other$old] <- T


########
# Some (13) remain
syn_empty <- syn[is.na(syn$GBIF_species),]
# Change
other <- data.frame(old = syn_empty$Name, GBIF = syn_empty$GBIF)

# Add
other$new_name <- c(NA, NA, "Crataegus coccinea", "Epimedium grandiflorum", NA, NA, NA, NA, "Rosa canina biserrata", NA, NA, NA, NA)
other$new_name[is.na(other$new_name)] <- other$GBIF[is.na(other$new_name)]

# Assign
syn$GBIF_species[syn$Name %in% other$old] <- other$new_name[match(syn$Name[syn$Name %in% other$old], other$old)]
syn$GBIF_genus[syn$Name %in% other$old] <- (vegdata::parse.taxa(other$new_name[match(syn$Name[syn$Name %in% other$old], other$old)])[[2]])
syn$GBIF[syn$Name %in% other$old] <- syn$GBIF_species[syn$Name %in% other$old]
syn$GBIF_rank[is.na(syn$GBIF_subspecies)] <- "SPECIES"
syn$GBIF_accepted[syn$Name %in% other$old] <- NA
syn$GBIF_ID[syn$Name %in% other$old] <- NA
syn$validated[syn$Name %in% other$old] <- T


# Check previously noticed errors
check <- syn[syn$GBIF %in%  c("Centaurea triumfettii semidecurrens", "Crataegus coccinea","Abelia grandiflora", 
                              "Pardoglossum cheirifolium cheirifolium", "Xanthoselinum alsaticum alsaticum", "Sedum candolleanum"),]


# Assign
syn$GBIF_ID <- as.integer(as.character(syn$GBIF_ID))
names_plantnet[names_plantnet$GBIF_Status == "SYNONYM" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),] <- syn
sum(is.na(names_plantnet$validated))
# 401 remain
```


### Doubtful
```{r}
# Check remaining status classes
doubt <- names_plantnet[names_plantnet$GBIF_Status == "DOUBTFUL" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),]

# check whether none are subspecies
gbif <-  name_backbone_checklist(doubt$Name[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(doubt$Name)/2*(i-1))
  end <- floor(length(doubt$GBIF)/2 * i)
  # run 
  data <- name_backbone_checklist(doubt$Name[begin: end])
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]
gbif_four <- gbif

# Assign subspecies
gbif$final <- gbif$subspecies


# Assign scientific name
gbif$scientificName[!is.na(gbif$acceptedScientificName)] <- gbif$acceptedScientificName[!is.na(gbif$acceptedScientificName)]
gbif$usageKey[!is.na(gbif$acceptedUsageKey)] <- gbif$acceptedUsageKey[!is.na(gbif$acceptedUsageKey)]


# Assign
gbif_doubt <- gbif[!is.na(gbif$status) & gbif$matchType %in% "EXACT",]
doubt[, 10:18] <- NA
# Subspecies
doubt$GBIF_subspecies <- gbif_doubt$final[match(doubt$Name, gbif_doubt$verbatim_name)]
doubt$GBIF_rank[!is.na(doubt$GBIF_subspecies)] <- "SUBSPECIES"
doubt$GBIF[!is.na(doubt$GBIF_subspecies)] <- doubt$GBIF_subspecies[!is.na(doubt$GBIF_subspecies)] 
doubt$GBIF_ID[!is.na(doubt$GBIF_subspecies)] <- gbif_doubt$usageKey[match(doubt$Name[!is.na(doubt$GBIF_subspecies)], gbif_doubt$verbatim_name)]
doubt$GBIF_accepted[!is.na(doubt$GBIF_subspecies)] <- gbif_doubt$scientificName[match(doubt$Name[!is.na(doubt$GBIF_subspecies)], gbif_doubt$verbatim_name)]
doubt$validated[!is.na(doubt$GBIF_subspecies)] <- T

# Species
doubt$GBIF_species <- gbif_doubt$species[match(doubt$Name, gbif_doubt$verbatim_name)]
doubt$GBIF_genus<- gbif_doubt$genus[match(doubt$Name, gbif_doubt$verbatim_name)]
doubt$GBIF_family <- gbif_doubt$family[match(doubt$Name, gbif_doubt$verbatim_name)]
doubt$GBIF_rank[doubt$Name %in% gbif_doubt$verbatim_name & is.na(doubt$GBIF_subspecies)] <- "SPECIES"
doubt$GBIF[doubt$Name %in% gbif_doubt$verbatim_name & is.na(doubt$GBIF_subspecies)]  <-  
  gbif_doubt$species[match(doubt$Name[doubt$Name %in% gbif_doubt$verbatim_name & is.na(doubt$GBIF_subspecies)]  , gbif_doubt$verbatim_name)]
doubt$GBIF_ID[doubt$Name %in% gbif_doubt$verbatim_name & is.na(doubt$GBIF_subspecies)]  <-  
  gbif_doubt$usageKey[match(doubt$Name[doubt$Name %in% gbif_doubt$verbatim_name & is.na(doubt$GBIF_subspecies)]  , gbif_doubt$verbatim_name)]
doubt$GBIF_accepted[doubt$Name %in% gbif_doubt$verbatim_name & is.na(doubt$GBIF_subspecies)]  <-  
  gbif_doubt$scientificName[match(doubt$Name[doubt$Name %in% gbif_doubt$verbatim_name & is.na(doubt$GBIF_subspecies)]  , gbif_doubt$verbatim_name)]
doubt$validated[doubt$Name %in% gbif_doubt$verbatim_name & is.na(doubt$GBIF_subspecies)] <- T


#######
# Some remain
doubt_empty <- doubt[is.na(doubt$GBIF_species),]
# Change
other <- data.frame(old = doubt_empty$Name, GBIF = doubt_empty$GBIF)

# Add
other$new_name <- c("Crepis blattarioides")

# Assign
doubt$GBIF_species[doubt$Name %in% other$old] <- other$new_name[match(doubt$Name[doubt$Name %in% other$old], other$old)]
doubt$GBIF_genus[doubt$Name %in% other$old] <- "Crepis"
doubt$GBIF[doubt$Name %in% other$old] <- doubt$GBIF_species[doubt$Name %in% other$old]
doubt$GBIF_rank[is.na(doubt$GBIF_subspecies)] <- "SPECIES"
doubt$GBIF_accepted[doubt$Name %in% other$old] <- NA
doubt$GBIF_ID[doubt$Name %in% other$old] <- NA
doubt$validated[doubt$Name %in% other$old] <- T


# Assign
doubt$GBIF_ID <- as.integer(as.character(doubt$GBIF_ID))
names_plantnet[names_plantnet$GBIF_Status == "DOUBTFUL" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),] <- doubt
sum(is.na(names_plantnet$validated))
# 233 remain
```


### Heterotypic synonym
```{r}
# Check remaining status classes
syn <- names_plantnet[names_plantnet$GBIF_Status %in% "HETEROTYPIC_SYNONYM" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),]
# Check whether none are subspecies
gbif <-  name_backbone_checklist(syn$Name[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(syn$Name)/2*(i-1))
  end <- floor(length(syn$GBIF)/2 * i)
  # run 
  data <- name_backbone_checklist(syn$Name[begin: end])
  gbif <- bind_rows(gbif, data)
}
# Save
gbif <- gbif[-1,]
gbif_five <- gbif

# Get final names
gbif$final <- gbif$subspecies

# Assign scientific name
gbif$scientificName[!is.na(gbif$acceptedScientificName)] <- gbif$acceptedScientificName[!is.na(gbif$acceptedScientificName)]
gbif$usageKey[!is.na(gbif$acceptedUsageKey)] <- gbif$acceptedUsageKey[!is.na(gbif$acceptedUsageKey)]


######
# Assign
gbif_syn <- gbif[!is.na(gbif$status) & gbif$matchType %in% "EXACT",]
syn[, 10:18] <- NA
# Subspecies
syn$GBIF_subspecies <- gbif_syn$final[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_rank[!is.na(syn$GBIF_subspecies)] <- "SUBSPECIES"
syn$GBIF[!is.na(syn$GBIF_subspecies)] <- syn$GBIF_subspecies[!is.na(syn$GBIF_subspecies)] 
syn$GBIF_ID[!is.na(syn$GBIF_subspecies)] <- gbif_syn$usageKey[match(syn$Name[!is.na(syn$GBIF_subspecies)], gbif_syn$verbatim_name)]
syn$GBIF_accepted[!is.na(syn$GBIF_subspecies)] <- gbif_syn$scientificName[match(syn$Name[!is.na(syn$GBIF_subspecies)], gbif_syn$verbatim_name)]
syn$validated[!is.na(syn$GBIF_subspecies)] <- T

# Species
syn$GBIF_species <- gbif_syn$species[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_genus<- gbif_syn$genus[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_family <- gbif_syn$family[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_rank[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)] <- "SPECIES"
syn$GBIF[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$species[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$GBIF_ID[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$usageKey[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$GBIF_accepted[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$scientificName[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$validated[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)] <- T


# Change some errors
other <- data.frame(old = c("Crepis conyzifolia", "Inula britannica", "Inula montana", "Inula salicina", "Orobanche ramosa", "Potentilla incana",
                   "Scorzonera austriaca", "Senecio jacobaea"),
           new_name = c("Crepis blattarioides", "Pentanema britannicum", "Pentanema montanum", "Pentanema salicinum", "Phelipanche ramosa", "Potentilla verna", 
                   "Takhtajaniantha austriaca", "Jacobaea vulgaris"))

# Assign
syn$GBIF_subspecies[syn$GBIF %in% other$old] <- other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)]
syn$GBIF_species[syn$GBIF %in% other$old] <- paste(vegdata::parse.taxa(other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]],
                                                       vegdata::parse.taxa(other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[3]])
syn$GBIF_genus[syn$GBIF %in% other$old] <- (vegdata::parse.taxa(other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]])
syn$GBIF[syn$GBIF %in% other$old] <- syn$GBIF_subspecies[syn$GBIF %in% other$old]
syn$GBIF_subspecies[syn$GBIF_subspecies == syn$GBIF_species ] <- NA
syn$GBIF_rank[!is.na(syn$GBIF_subspecies)] <- "SUBSPECIES"
syn$GBIF_accepted[syn$Name %in% other$old] <- NA
syn$GBIF_ID[syn$Name %in% other$old] <- NA
syn$validated[syn$Name %in% other$old] <- T

# How many not ready yet (67)
sum(is.na(syn$GBIF_genus))



#######
# Some are already saved previously
saved <- names_plantnet[!is.na(names_plantnet$validated),]
saved <- saved[saved$Name %in% syn$Name,]
# Assign
syn$GBIF_species[syn$Name %in% saved$Name] <- saved$GBIF_species[match(syn$Name[syn$Name %in% saved$Name], saved$Name)]
syn$GBIF_genus[syn$Name %in% saved$Name] <- saved$GBIF_genus[match(syn$Name[syn$Name %in% saved$Name], saved$Name)]
syn$GBIF_family[syn$Name %in% saved$Name] <- saved$GBIF_family[match(syn$Name[syn$Name %in% saved$Name], saved$Name)]
syn$GBIF_accepted[syn$Name %in% saved$Name] <- saved$GBIF_accepted[match(syn$Name[syn$Name %in% saved$Name], saved$Name)]
syn$GBIF_ID[syn$Name %in% saved$Name] <- saved$GBIF_ID[match(syn$Name[syn$Name %in% saved$Name], saved$Name)]
syn$validated[syn$Name %in% saved$Name] <- saved$validated[match(syn$Name[syn$Name %in% saved$Name], saved$Name)]
syn$GBIF_rank[syn$Name %in% saved$Name] <- saved$GBIF_rank[match(syn$Name[syn$Name %in% saved$Name], saved$Name)]

# How many not ready yet (66)
sum(is.na(syn$GBIF_genus))



########
# Remaining have to be checked
syn_missing <- syn[is.na(syn$validated),]
gbif_incorrect <- gbif[gbif$verbatim_name %in% syn_missing$Name,]

# We will verify manually (66)
change <- data.frame(old= syn_missing$GBIF, new= syn_missing$GBIF_species)
change$new <- names_plantnet$GBIF_species[match(change$old, names_plantnet$Name)]

# Some have to be changed or kept
keep <- change[c(1,2, 3, 4, 9, 19, 25, 27, 29, 31, 33, 36, 53, 65),]
other <- change[c(5, 7, 10, 13, 16, 18, 22, 37, 38, 45, 46, 47, 49,51, 58, 64),]
change <- change[c(6, 8, 11, 12, 14, 15, 17, 20, 21, 23, 24, 26, 28, 
                   30, 32, 34, 35, 39, 40, 41, 42, 43, 44, 48, 50,
                   52, 54, 55, 56, 57, 59, 60, 61, 62, 63, 66), ]

# Update the other
other$final <- c("Pulsatilla halleri halleri", "Apocynum cannabinum", "Asplenium laciniatum laciniatum", "Mahonia aquifolium",
                 "Centaurea stoebe stoebe", "Polanisia dodecandra dodecandra", "Chamaenerion angustifolium angustifolium", "Orobanche camptolepis", 
                 "Phelipanche purpurea purpurea", "Prunus domestica insititia", "Myosurus minimus minimus", "Ranunculus polyanthemos nemorosus", "Atadinus pumilus pumilus",
                 "Caroxylon vermiculatum", "Aria latifolia", "Valerianella locusta locusta")
syn$GBIF_subspecies[syn$GBIF %in% other$old] <- other$final[match(syn$GBIF[syn$GBIF %in% other$old], other$old)]
syn$GBIF_species[syn$GBIF %in% other$old] <- paste(vegdata::parse.taxa(other$final[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]],
                                                       vegdata::parse.taxa(other$final[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[3]])
syn$GBIF_genus[syn$GBIF %in% other$old] <- (vegdata::parse.taxa(other$final[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]])
syn$GBIF[syn$GBIF %in% other$old] <- syn$GBIF_subspecies[syn$GBIF %in% other$old]
syn$GBIF_subspecies[syn$GBIF_subspecies == syn$GBIF_species] <- NA
syn$GBIF_rank[!is.na(syn$GBIF_subspecies)] <- "SUBSPECIES"
syn$GBIF_rank[is.na(syn$GBIF_subspecies) & syn$Name %in% other$old] <- "SPECIES"
syn$GBIF_accepted[syn$GBIF %in% other$final] <- NA
syn$GBIF_ID[syn$GBIF %in% other$final] <- NA
syn$validated[syn$GBIF %in% other$final] <- T

# Change the ones found
syn$GBIF_species[syn$GBIF %in% change$old] <- change$new[match(syn$GBIF[syn$GBIF %in% change$old], change$old)]
syn$GBIF_genus[syn$GBIF %in% change$old] <- (vegdata::parse.taxa(change$new[match(syn$GBIF[syn$GBIF %in% change$old], change$old)])[[2]])
syn$GBIF_rank[syn$GBIF %in% change$old] <- "SPECIES"
syn$GBIF[syn$GBIF %in% change$old] <- change$new[match(syn$GBIF[syn$GBIF %in% change$old], change$old)]
syn$GBIF_accepted[syn$Name %in% change$old] <- NA
syn$GBIF_ID[syn$Name %in% change$old] <- NA
syn$validated[syn$Name %in% change$old] <- T


# Change the ones correct
syn$GBIF_species[syn$GBIF %in% keep$old] <- keep$old[match(syn$GBIF[syn$GBIF %in% keep$old], keep$old)]
syn$GBIF_genus[syn$GBIF %in% keep$old] <- (vegdata::parse.taxa(keep$old[match(syn$GBIF[syn$GBIF %in% keep$old], keep$old)])[[2]])
syn$GBIF_rank[syn$GBIF %in% keep$old] <- "SPECIES"
syn$GBIF[syn$GBIF %in% keep$old] <- keep$old[match(syn$GBIF[syn$GBIF %in% keep$old], keep$old)]
syn$GBIF_accepted[syn$GBIF %in% keep$old] <- NA
syn$GBIF_ID[syn$GBIF %in% keep$old] <- NA
syn$validated[syn$GBIF %in% keep$old] <- T

# How many remain
sum(is.na(syn$validated))


# Assign
syn$GBIF_ID <- as.integer(as.character(syn$GBIF_ID))
names_plantnet[names_plantnet$GBIF_Status %in% "HETEROTYPIC_SYNONYM" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),] <- syn
sum(is.na(names_plantnet$validated))
# 116
```


### Homotypic synonym
```{r}
# Check remaining status classes
syn <- names_plantnet[names_plantnet$GBIF_Status == "HOMOTYPIC_SYNONYM" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),]

# check whether none are subspecies
gbif <-  name_backbone_checklist(syn$Name[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(syn$Name)/2*(i-1))
  end <- floor(length(syn$Name)/2 * i)
  # run 
  data <- name_backbone_checklist(syn$Name[begin: end])
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]
gbif_six <- gbif


# Get final names
gbif$final <- gbif$subspecies

# Assign scientific name
gbif$scientificName[!is.na(gbif$acceptedScientificName)] <- gbif$acceptedScientificName[!is.na(gbif$acceptedScientificName)]
gbif$usageKey[!is.na(gbif$acceptedUsageKey)] <- gbif$acceptedUsageKey[!is.na(gbif$acceptedUsageKey)]


######
# Assign
gbif_syn <- gbif[!is.na(gbif$status) & gbif$matchType %in% "EXACT",]
syn[, 10:18] <- NA
# Subspecies
syn$GBIF_subspecies <- gbif_syn$final[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_rank[!is.na(syn$GBIF_subspecies)] <- "SUBSPECIES"
syn$GBIF[!is.na(syn$GBIF_subspecies)] <- syn$GBIF_subspecies[!is.na(syn$GBIF_subspecies)] 
syn$GBIF_ID[!is.na(syn$GBIF_subspecies)] <- gbif_syn$usageKey[match(syn$Name[!is.na(syn$GBIF_subspecies)], gbif_syn$verbatim_name)]
syn$GBIF_accepted[!is.na(syn$GBIF_subspecies)] <- gbif_syn$scientificName[match(syn$Name[!is.na(syn$GBIF_subspecies)], gbif_syn$verbatim_name)]
syn$validated[!is.na(syn$GBIF_subspecies)] <- T

# Species
syn$GBIF_species <- gbif_syn$species[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_genus<- gbif_syn$genus[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_family <- gbif_syn$family[match(syn$Name, gbif_syn$verbatim_name)]
syn$GBIF_rank[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)] <- "SPECIES"
syn$GBIF[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$species[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$GBIF_ID[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$usageKey[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$GBIF_accepted[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  <-  
  gbif_syn$scientificName[match(syn$Name[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)]  , gbif_syn$verbatim_name)]
syn$validated[syn$Name %in% gbif_syn$verbatim_name & is.na(syn$GBIF_subspecies)] <- T


# Change some errors
other <- data.frame(old = c("Senega cyparissias", "Microseris alpestris", "Merremia umbellata", "Leontodon rothii", "Coincya tournefortii", "Hieracium intybaceum"),
                    new_name = c("Senega cyparissias", "Nothocalais alpestris", "Camonea pilosa", "Leontodon longirostris", "Coincya tournefortii", "Crepis blattarioides"))

# Assign
syn$GBIF_species[syn$Name %in% other$old] <- other$new_name[match(syn$Name[syn$Name %in% other$old], other$old)]
syn$GBIF_genus[syn$Name %in% other$old] <- (vegdata::parse.taxa(other$new_name[match(syn$GBIF[syn$GBIF %in% other$old], other$old)])[[2]])
syn$GBIF[syn$Name %in% other$old] <- syn$GBIF_species[syn$Name %in% other$old]
syn$GBIF_rank[is.na(syn$GBIF_subspecies)] <- "SPECIES"
syn$GBIF_accepted[syn$Name %in% other$old] <- NA
syn$GBIF_ID[syn$Name %in% other$old] <- NA
syn$validated[syn$Name %in% other$old] <- T

# How many not ready yet
sum(is.na(syn$GBIF_genus))



# Assign
syn$GBIF_subspecies[syn$Name %in% c("Osmunda claytoniana")] <- "Claytosmunda claytoniana claytoniana"
syn$GBIF_species[syn$Name %in% c("Osmunda claytoniana")] <- "Claytosmunda claytoniana"
syn$GBIF[syn$Name %in% c("Osmunda claytoniana")] <- "Claytosmunda claytoniana claytoniana"
syn$GBIF_genus[syn$Name %in% c("Osmunda claytoniana")] <- "Claytosmunda"
syn$GBIF_accepted[syn$Name %in% c("Osmunda claytoniana")] <- NA
syn$GBIF_ID[syn$Name %in% c("Osmunda claytoniana")] <- NA


# Assign
syn$GBIF_ID <- as.integer(as.character(syn$GBIF_ID))
names_plantnet[names_plantnet$GBIF_Status == "HOMOTYPIC_SYNONYM" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),] <- syn
sum(is.na(names_plantnet$validated))
# 92 remain
```


### Proparte synonym
```{r}
# Which remain
remaining <- names_plantnet[is.na(names_plantnet$validated),]


#######
# Check Proparte synonyms
check <- names_plantnet[names_plantnet$GBIF_Status == "PROPARTE_SYNONYM" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),]

# Most are accepted, except these two
change <- data.frame(new = c("Rhinanthus serotinus serotinus", "Sagina alexandrae", "Rosa pendulina", "Rhinanthus glacialis", "Luffa aegyptiaca"), 
                     old = c("Rhinanthus major","Sagina subulata", "Rosa cinnamomea", "Rhinanthus angustifolius", "Luffa cylindrica"))

# Change these
check$GBIF_subspecies[check$Name %in% change$old] <- change$new[match(check$Name[check$Name %in% change$old], change$old)]
check$GBIF_species[check$Name %in% change$old] <- paste(vegdata::parse.taxa(check$GBIF_subspecies[!is.na(check$GBIF_subspecies)])[[2]],
                                                        vegdata::parse.taxa(check$GBIF_subspecies[!is.na(check$GBIF_subspecies)])[[3]])
check$GBIF[check$Name %in% change$old] <- change$new[match(check$Name[check$Name %in% change$old], change$old)]
check$GBIF_subspecies[check$GBIF_subspecies == check$GBIF_species] <- NA
check$GBIF_ID[check$Name %in% change$old] <- NA
check$GBIF_accepted[check$Name %in% change$old] <- NA

# Change the others
check$GBIF[!check$Name %in% change$old] <- check$GBIF_species[!check$Name %in% change$old] 
check$GBIF_genus <- vegdata::parse.taxa(check$GBIF_species)[[2]]
check$validated <- T

# Assign
names_plantnet[names_plantnet$GBIF_Status == "PROPARTE_SYNONYM" & !is.na(names_plantnet$GBIF) & is.na(names_plantnet$validated),] <- check 
# How many remain --> 84 still
sum(is.na(names_plantnet$validated))
```


### Remaining
```{r}
# Get all the last ones
remaining <- names_plantnet[is.na(names_plantnet$validated),]
# These are all missing a GBIF ID number, run again through GBIF

# Many are genera with spp. as an indicator
# Remove spp. and check again against gbif
remaining$new_name <- gsub(" spp.","", remaining$Name)
gbif <-  name_backbone_checklist(remaining$new_name[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(remaining$new_name)/2*(i-1))
  end <- floor(length(remaining$new_name)/2 * i)
  # run 
  data <- name_backbone_checklist(remaining$new_name[begin: end])
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]
gbif_seven <- gbif


# Get final names
gbif$final <- gbif$subspecies

# Assign scientific name
gbif$scientificName[!is.na(gbif$acceptedScientificName)] <- gbif$acceptedScientificName[!is.na(gbif$acceptedScientificName)]
gbif$usageKey[!is.na(gbif$acceptedUsageKey)] <- gbif$acceptedUsageKey[!is.na(gbif$acceptedUsageKey)]


######
# Assign
gbif_acc <- gbif[!is.na(gbif$status) & gbif$matchType %in% "EXACT",]
remaining[, 10:18] <- NA
# Subspecies
remaining$GBIF_subspecies <- gbif_acc$final[match(remaining$new_name, gbif_acc$verbatim_name)]
remaining$GBIF_rank[!is.na(remaining$GBIF_subspecies)] <- "SUBSPECIES"
remaining$GBIF[!is.na(remaining$GBIF_subspecies)] <- remaining$GBIF_subspecies[!is.na(remaining$GBIF_subspecies)] 
remaining$GBIF_ID[!is.na(remaining$GBIF_subspecies)] <- gbif_acc$usageKey[match(remaining$new_name[!is.na(remaining$GBIF_subspecies)], gbif_acc$verbatim_name)]
remaining$GBIF_accepted[!is.na(remaining$GBIF_subspecies)] <- gbif_acc$scientificName[match(remaining$new_name[!is.na(remaining$GBIF_subspecies)], gbif_acc$verbatim_name)]
remaining$validated[!is.na(remaining$GBIF_subspecies)] <- T

# Species
remaining$GBIF_species <- gbif_acc$species[match(remaining$new_name, gbif_acc$verbatim_name)]
remaining$GBIF_genus<- gbif_acc$genus[match(remaining$new_name, gbif_acc$verbatim_name)]
remaining$GBIF_family <- gbif_acc$family[match(remaining$new_name, gbif_acc$verbatim_name)]
remaining$GBIF_rank[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_subspecies)] <- "SPECIES"
remaining$GBIF_rank[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_species)] <- "GENUS"
remaining$GBIF[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_subspecies)]  <-  
  gbif_acc$species[match(remaining$new_name[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_subspecies)]  , gbif_acc$verbatim_name)]
remaining$GBIF[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_species)]  <-  
  gbif_acc$genus[match(remaining$new_name[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_species)]  , gbif_acc$verbatim_name)]
remaining$GBIF_ID[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_subspecies)]  <-  
  gbif_acc$usageKey[match(remaining$new_name[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_subspecies)]  , gbif_acc$verbatim_name)]
remaining$GBIF_accepted[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_subspecies)]  <-  
  gbif_syn$scientificName[match(remaining$new_name[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_subspecies)]  , gbif_acc$verbatim_name)]
remaining$validated[remaining$new_name %in% gbif_acc$verbatim_name & is.na(remaining$GBIF_subspecies)] <- T

# How many remain
sum(is.na(remaining$GBIF))


# Assign the rest
remaining$GBIF_ID <- as.integer(as.character(remaining$GBIF_ID))
names_plantnet[is.na(names_plantnet$validated),] <- remaining[, 1:18]
```


```{r}
# Get all the last ones
remaining <- names_plantnet[is.na(names_plantnet$validated),]
remaining$old <- gsub(" spp.","", remaining$Name)

# Some have to be adapted
change <- remaining[c(3, 9, 15, 16, 17, 20, 21, 30, 32, 36, 37),]
change$new <- c("Begonia cucullata","Fragaria", "Anacis major", "Anacis tripteris", "Anacis verticillata", "Rhamphospermum arvense", 
                "Rhamphospermum carinatum", "Podophyllum", "Psidium cattleianum","Dracaena" ,"Taraxacum")

# Change the ones found
remaining$GBIF_species[remaining$old %in% change$old] <- change$new[match(remaining$old[remaining$old %in% change$old], change$old)]
remaining$GBIF_species[is.na(remaining$GBIF_species)] <- remaining$old[is.na(remaining$GBIF_species)] 
remaining$GBIF_genus <- (vegdata::parse.taxa(remaining$GBIF_species)[[2]])
remaining$GBIF <- remaining$GBIF_species
remaining$GBIF_species[remaining$GBIF_species == remaining$GBIF_genus] <- NA
remaining$GBIF_rank[!is.na(remaining$GBIF_species)] <- "SPECIES"
remaining$GBIF_rank[is.na(remaining$GBIF_species)] <- "GENUS"
remaining$validated <- T

# Assign
names_plantnet[is.na(names_plantnet$validated),] <- remaining[, c(1:18)]

# Some genera are previously not assigned, now do it
# names_plantnet$GBIF_genus[is.na(names_plantnet$GBIF_genus)] <- vegdata::parse.taxa(names_plantnet$GBIF_species[is.na(names_plantnet$GBIF_genus)])[[2]]
names_plantnet$GBIF_accepted[names_plantnet$GBIF_rank %in% "GENUS"] <- NA
names_plantnet$GBIF_rank[!is.na(names_plantnet$GBIF_subspecies)] <- "SUBSPECIES"
```


### Families
```{r}
# Get dataframe of genera 
genera <- names_plantnet |> group_by(GBIF_genus, GBIF_family) |> summarise(n = n())
genera <- genera[!is.na(genera$GBIF_family),1:2]
dup <- genera[duplicated(genera$GBIF_genus) | duplicated(genera$GBIF_genus, fromLast = T),]
dup <- dup[c(2,3, 6),]
# Change these
names_plantnet$GBIF_family[names_plantnet$GBIF_genus %in% dup$GBIF_genus] <- 
  dup$GBIF_family[match(names_plantnet$GBIF_genus[names_plantnet$GBIF_genus %in% dup$GBIF_genus], dup$GBIF_genus)]
# Get again
genera <- names_plantnet |> group_by(GBIF_genus, GBIF_family) |> summarise(n = n())
genera <- genera[!is.na(genera$GBIF_family),1:2]

# Missing families
fam_mis <- names_plantnet[is.na(names_plantnet$GBIF_family),]
fam_mis$GBIF_family <- genera$GBIF_family[match(fam_mis$GBIF_genus, genera$GBIF_genus)]
fam_mis$GBIF_family[is.na(fam_mis$GBIF_family)] <- fam_mis$Family[is.na(fam_mis$GBIF_family)]
# Assign
names_plantnet[is.na(names_plantnet$GBIF_family),] <- fam_mis
```


### GBIF_ID
```{r}
########
# We will look whether we can assign new ID's or accepted names (232)
non_acc <- names_plantnet[is.na(names_plantnet$GBIF_accepted),]
# Look for accepted names
acc <-  names_plantnet[!is.na(names_plantnet$GBIF_accepted),]

# Assign
non_acc$GBIF_accepted <- acc$GBIF_accepted[match(non_acc$GBIF, acc$GBIF)]
non_acc$GBIF_ID <- acc$GBIF_ID[match(non_acc$GBIF, acc$GBIF)]


# Assign also keys for genera etc
genera <- names_plantnet[names_plantnet$GBIF_rank %in% "GENUS",]
gbif <-  name_backbone_checklist(genera$GBIF[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(genera$GBIF)/2*(i-1))
  end <- floor(length(genera$GBIF)/2 * i)
  # run 
  data <- name_backbone_checklist(genera$GBIF[begin: end])
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]
gbif_eight <- gbif

# assign these keys
non_acc$GBIF_ID[is.na(non_acc$GBIF_ID)]  <- gbif$genusKey[match(non_acc$GBIF[is.na(non_acc$GBIF_ID)], gbif$verbatim_name)]
non_acc$GBIF_accepted[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)]  <- 
  gbif$scientificName[match(non_acc$GBIF[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)], gbif$verbatim_name)]

# Assign
non_acc$GBIF_ID <- as.integer(as.character(non_acc$GBIF_ID))
names_plantnet[is.na(names_plantnet$GBIF_accepted),] <- non_acc


######
# Get the remaining GBIF ID's (125)
non_acc <- names_plantnet[is.na(names_plantnet$GBIF_ID) & !duplicated(names_plantnet$GBIF) ,]

# Create a list
gbif_list <- vector("list", nrow(non_acc))

# Run function to get ID's
for(i in 1:nrow(non_acc)){
  res <- tryCatch(get_gbifid_(non_acc$GBIF[i])[[1]], error = function(e) NULL)
  if(is.null(res) || nrow(res) == 0) {
    gbif_list[[i]] <- data.frame(query = non_acc$GBIF[i], usagekey = NA, status = NA)
  } else {
    res$query <- non_acc$GBIF[i]   # keep track of which input name this came from
    gbif_list[[i]] <- res
  }
}

# Combine all data
gbif_candidates <- bind_rows(gbif_list)

# Look at the data that is supposed to be exactly the same
gbif_candidates <- gbif_candidates[gbif_candidates$matchtype %in% "EXACT",]
# Remove the duplicated ones
dup <- gbif_candidates[duplicated(gbif_candidates$query),]
already_fine <- gbif_candidates[!gbif_candidates$query %in% dup$query,]

# These can already be assigned
non_acc$GBIF_ID[is.na(non_acc$GBIF_ID)]  <- already_fine$usagekey[match(non_acc$GBIF[is.na(non_acc$GBIF_ID)], already_fine$query)]
non_acc$GBIF_accepted[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)]  <- 
  already_fine$scientificname[match(non_acc$GBIF[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)], already_fine$query)]

# Look at remaining
gbif_candidates <- gbif_candidates[!gbif_candidates$query %in% already_fine$query,]
# Look at accepted
gbif_candidates <- gbif_candidates[gbif_candidates$status %in% "ACCEPTED",]
dup <- gbif_candidates[duplicated(gbif_candidates$query),]
already_fine <- gbif_candidates[!gbif_candidates$query %in% dup$query,]
# These can already be assigned
non_acc$GBIF_ID[is.na(non_acc$GBIF_ID)]  <- already_fine$usagekey[match(non_acc$GBIF[is.na(non_acc$GBIF_ID)], already_fine$query)]
non_acc$GBIF_accepted[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)]  <- 
  already_fine$scientificname[match(non_acc$GBIF[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)], already_fine$query)]

# Look at remaining
gbif_candidates <- gbif_candidates[!gbif_candidates$query %in% already_fine$query,]
choice <- c("Betonica officinalis subsp. officinalis","Cymbidium Sw.","Dahlia Cav.", "Dracaena Vand. ex L.", "Echinopsis Zucc.", "Ficaria verna subsp. verna", "Ficus L.",
            "Pulicaria arabica subsp. hispanica (Boiss.) Murb.","Rhinanthus serotinus subsp. serotinus", "Salix L.", "Taraxacum Weber", "Viola L.")
already_fine <- gbif_candidates[gbif_candidates$scientificname %in% choice,]
# These can already be assigned
non_acc$GBIF_ID[is.na(non_acc$GBIF_ID)]  <- already_fine$usagekey[match(non_acc$GBIF[is.na(non_acc$GBIF_ID)], already_fine$query)]
non_acc$GBIF_accepted[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)]  <- 
  already_fine$scientificname[match(non_acc$GBIF[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)], already_fine$query)]



# Combine all data again
gbif_candidates <- bind_rows(gbif_list)
gbif_candidates <- gbif_candidates[!gbif_candidates$query %in% non_acc$GBIF[!is.na(non_acc$GBIF_ID)],]
gbif_candidates <- gbif_candidates[gbif_candidates$matchtype %in% "EXACT",]

# We will just also choose from these
choice <- c("Alchemilla arvensis L.", "Allium cirrhosum Vand.", "Allium porrum L.", "Alopecurus gerardii (All.) Vill.", "Amelanchier spicata (Lam.) K.Koch", 
            "Asarum virginicum L.", "Convolvulus soldanella L.", "Cynoglossum lanceolatum Forssk.", "Draba muralis L.", "Eruca vesicaria subsp. sativa (Mill.) Thell.", 
            "Erysimum ochroleucum (Schleich.) DC.", "Festuca arundinacea Schreb.", "Galium corrudifolium Vill.", "Genista aetnensis (Biv.) DC.", 
            "Hieracium megalocephalon Nash", "Hydrangea × versicolor (Fortune) J.M.H.Shaw", "Hypochaeris uniflora Vill.", "Iris latifolia (Mill.) Voss", 
            "Justicia procumbens L.", "Leontodon saxatilis Lam.", "Melaleuca citrina (Curtis) Dum.Cours.", "Rhamphospermum arvense (L.) Andrz. ex Besser", 
            "Phoebanthus grandiflora (Torr. & A.Gray) S.F.Blake", "Rhaponticum centauroides (L.) O.Bolòs", "Sanguisorba verrucosa (G.Don) Ces.", 
            "Schedonorus arundinaceus (Schreb.) Dumort.", "Sorbus aria (L.) Crantz", "Aria latifolia (Lam.) M.Roem.","Vicia angustifolia L.")

# Assign
already_fine <- gbif_candidates[gbif_candidates$scientificname %in% choice,]
# These can already be assigned
non_acc$GBIF_ID[is.na(non_acc$GBIF_ID)]  <- already_fine$usagekey[match(non_acc$GBIF[is.na(non_acc$GBIF_ID)], already_fine$query)]
non_acc$GBIF_accepted[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)]  <- 
  already_fine$scientificname[match(non_acc$GBIF[is.na(non_acc$GBIF_accepted) & !is.na(non_acc$GBIF_ID)], already_fine$query)]


# Assign also keys for genera etc
non_acc_assign <- names_plantnet[is.na(names_plantnet$GBIF_ID) ,]
non_acc_assign$GBIF_accepted <- non_acc$GBIF_accepted[match(non_acc_assign$GBIF, non_acc$GBIF)]
non_acc_assign$GBIF_ID <- non_acc$GBIF_ID[match(non_acc_assign$GBIF, non_acc$GBIF)]

# Assign
non_acc_assign$GBIF_ID <- as.integer(as.character(non_acc_assign$GBIF_ID))
names_plantnet[is.na(names_plantnet$GBIF_ID) ,]<- non_acc_assign


###
# Change some that were still incorrect
names_plantnet$GBIF[names_plantnet$GBIF %in% "Berberis japonica"] <- "Mahonia japonica"
names_plantnet$GBIF_species[names_plantnet$GBIF %in%  "Gyrophyllum major"] <- "Anacis major"
names_plantnet$GBIF_genus[names_plantnet$GBIF %in% "Gyrophyllum major"] <- "Anacis"
names_plantnet$GBIF[names_plantnet$GBIF %in% "Gyrophyllum major"] <- "Anacis major"

# We will look whether we can assign new ID's or accepted names
non_acc <- names_plantnet[is.na(names_plantnet$GBIF_accepted),]
# Look for accepted names
acc <-  names_plantnet[!is.na(names_plantnet$GBIF_accepted),]

# Assign
non_acc$GBIF_accepted <- acc$GBIF_accepted[match(non_acc$GBIF, acc$GBIF)]
non_acc$GBIF_ID <- acc$GBIF_ID[match(non_acc$GBIF, acc$GBIF)]

# Change
change <- data.frame(old = non_acc$GBIF[is.na(non_acc$GBIF_accepted)],
                     new = c("Alopecurus gerardi Vill.","Genista etnensis (Raf.) DC.","Anacis major (Walter) Z.H.Feng, Z.J.Huang & Su Liu",
                             "Anacis major (Walter) Z.H.Feng, Z.J.Huang & Su Liu", "Anacis verticillata (L.) Z.H.Feng, Z.J.Huang & Su Liu", 
                             "Meiosperma bracteatum (Hochst.) I.Darbysh. & E.A.Tripp", "Hieracium megacephalon Nash","Rhamphospermum carinatum A.Braun comb. ined.", 
                             "Oreomecon crocea (Ledeb.) Banfi, Bartolucci, J.-M.Tison & Galasso", "Oreomecon lapponica (Tolm.) Galasso, Banfi & Bartolucci", 
                             "Oreomecon olchonensis (Peschkova) Galasso, Banfi & Bartolucci", "Oreomecon radicata (Rottb.) Banfi, Bartolucci, J.-M.Tison & Galasso",
                             "Claytosmunda claytoniana subsp. vestita (Milde) Lehnert", "Phoebanthus grandiflorus (Torr. & A. Gray) S. F. Blake",
                             "Salimenaea integrifolia (Griseb.) N.O'Leary & P.Moroni", 
                             "Troncosoa seriphioides (A.Gray) N.O'Leary & P.Moroni", "Valeriana orientalis (DC.) Sennikov"))

# Assign
non_acc$GBIF_accepted[is.na(non_acc$GBIF_ID)] <- change$new[match(non_acc$GBIF[is.na(non_acc$GBIF_ID)], change$old)]
non_acc$GBIF_ID <- as.integer(as.character(non_acc$GBIF_ID))
names_plantnet[is.na(names_plantnet$GBIF_accepted),] <- non_acc

# All names are assigned
```

### ID
```{r}
# 17 have no ID yet
non_acc <- names_plantnet[is.na(names_plantnet$GBIF_ID),]
# Check with GBIF
gbif <-  name_backbone_checklist(non_acc$GBIF_accepted[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(non_acc$GBIF_accepted)/2*(i-1))
  end <- floor(length(non_acc$GBIF_accepted)/2 * i)
  # run 
  data <- name_backbone_checklist(non_acc$GBIF_accepted[begin: end])
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]
# Some do now have an ID
gbif <- gbif[gbif$verbatim_name %in% c("Alopecurus gerardi Vill.","Hieracium megacephalon Nash","Phoebanthus grandiflorus (Torr. & A. Gray) S. F. Blake"),]

# Assign
non_acc$GBIF_ID <- gbif$usageKey[match(non_acc$GBIF_accepted, gbif$verbatim_name)]
non_acc$GBIF_ID <- as.integer(as.character(non_acc$GBIF_ID))
names_plantnet[is.na(names_plantnet$GBIF_ID),] <- non_acc
```




## 3.4 Check
### Duplicates
```{r}
#######
# Duplicates in family
dup <- names_plantnet |> group_by(GBIF_genus, GBIF_family) |> summarise(n = n())
dup <- dup[duplicated(dup$GBIF_genus) | duplicated(dup$GBIF_genus, fromLast = T),]
names_plantnet$GBIF_family[names_plantnet$GBIF_genus %in% dup$GBIF_genus] <- "Blechnaceae"
# Fixed


#######
# Duplicates in genus
dup <- names_plantnet |> group_by(GBIF_species, GBIF_genus, GBIF_family) |> summarise(n = n())
dup <- dup[duplicated(dup$GBIF_species) | duplicated(dup$GBIF_species, fromLast = T),]
dup <- dup[!is.na(dup$GBIF_species),]
# Two are incorrect
dup_correct <- dup[dup$GBIF_genus == vegdata::parse.taxa(dup$GBIF_species)[[2]],]
names_plantnet$GBIF_family[names_plantnet$GBIF_species %in% dup_correct$GBIF_species] <- 
  dup_correct$GBIF_family[match(names_plantnet$GBIF_species[names_plantnet$GBIF_species %in% dup_correct$GBIF_species], dup_correct$GBIF_species)]
names_plantnet$GBIF_genus[names_plantnet$GBIF_species %in% dup_correct$GBIF_species] <- 
  dup_correct$GBIF_genus[match(names_plantnet$GBIF_species[names_plantnet$GBIF_species %in% dup_correct$GBIF_species], dup_correct$GBIF_species)]
# Fixed


#######
# Duplicates in species
dup <- names_plantnet |> group_by(GBIF_subspecies, GBIF_species, GBIF_genus, GBIF_family) |> summarise(n = n())
dup <- dup[duplicated(dup$GBIF_subspecies) | duplicated(dup$GBIF_subspecies, fromLast = T),]
dup <- dup[!is.na(dup$GBIF_subspecies),]
# These are all correct!



#######
# Duplicates in rank
dup <- names_plantnet |> group_by(GBIF_rank, GBIF_subspecies, GBIF_species, GBIF_genus, GBIF_family) |> summarise(n = n())
dup <- dup[duplicated(dup$GBIF_species) | duplicated(dup$GBIF_species, fromLast = T),]
# None seem incorrect

# Duplicates in rank
dup <- names_plantnet |> group_by(GBIF, GBIF_rank, GBIF_subspecies, GBIF_species, GBIF_genus, GBIF_family) |> summarise(n = n())
dup <- dup[duplicated(dup$GBIF) | duplicated(dup$GBIF, fromLast = T),]
dup_correct <- dup[c(2),]
# Assign
names_plantnet$GBIF_subspecies[names_plantnet$GBIF %in% dup_correct$GBIF] <- dup_correct$GBIF_subspecies
names_plantnet$GBIF_species[names_plantnet$GBIF %in% dup_correct$GBIF] <- dup_correct$GBIF_species
names_plantnet$GBIF_rank[names_plantnet$GBIF %in% dup_correct$GBIF] <- dup_correct$GBIF_rank
```


### Ranks Plantnet
```{r}
# We will subdivide between the original data and the final data
names_plantnet$GBIF_rank[grepl("sect\\.", names_plantnet$GBIF_accepted)] <- "SECTOR"
names_plantnet$GBIF_rank[grepl("cv\\.", names_plantnet$GBIF_accepted)] <- "CULTIVAR"
names_plantnet$GBIF_rank[grepl("subsp\\.", names_plantnet$GBIF_accepted)] <- "SUBSPECIES"
names_plantnet$GBIF_rank[grepl(" x ", names_plantnet$GBIF_accepted)] <- "HYBRID"
names_plantnet$GBIF_rank[grepl("×", names_plantnet$GBIF_accepted)] <- "HYBRID"


# Save plantnet names
#write_csv(names_plantnet, "../Extra/Intermediate/Plantnet_names_cleaning_newest_newest.csv")
```


### Final name
```{r}
# Get final name
names_plantnet_extra <- names_plantnet
names_plantnet_extra$final <- names_plantnet_extra$GBIF_subspecies
names_plantnet_extra$final[is.na(names_plantnet_extra$final)] <- names_plantnet_extra$GBIF_species[is.na(names_plantnet_extra$final)] 
names_plantnet_extra$final[is.na(names_plantnet_extra$final)] <- names_plantnet_extra$GBIF_genus[is.na(names_plantnet_extra$final)] 

# Check which differ
check <- names_plantnet_extra[names_plantnet_extra$GBIF != names_plantnet_extra$final, ]
# They are always the same, perfect
```



## 3.5 Save
```{r}
pol_plantnet$GBIF_subspecies <- names_plantnet$GBIF_subspecies[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_species <- names_plantnet$GBIF_species[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_genus <- names_plantnet$GBIF_genus[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_family <- names_plantnet$GBIF_family[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_ID_final<- names_plantnet$GBIF_ID[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_accepted_name <- names_plantnet$GBIF_accepted[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_name <- names_plantnet$GBIF[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_rank <- names_plantnet$GBIF_rank[match(pol_plantnet$Name, names_plantnet$Name)]

#write_csv(pol_plantnet, "../Results/Plantnet_identification_all.csv")
#pol_plantnet <- read_csv( "../Results/Plantnet_identification_all.csv", show_col_types = FALSE)
```




```{r}
# We will assign to the original database
all_data$Plantnet_subspecies <- pol_plantnet$GBIF_subspecies[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_species <- pol_plantnet$GBIF_species[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_genus <- pol_plantnet$GBIF_genus[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_family <- pol_plantnet$GBIF_family[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plant_plantnet <- pol_plantnet$GBIF_name[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_rank <- pol_plantnet$GBIF_rank[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_GBIF_ID <- pol_plantnet$GBIF_ID_final[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_GBIF_accepted_name <- pol_plantnet$GBIF_accepted_name[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_organ <- pol_plantnet$Organ[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_score <- pol_plantnet$Score[match(all_data$Obs_ID, pol_plantnet$ID)]

# Check number of species again
check <- all_data |> distinct(Plant_plantnet, Plantnet_rank, Plantnet_subspecies, Plantnet_species, Plantnet_genus, Plantnet_family)
all_data_save <- all_data
all_data <- all_data_save
```




# USER
## 4.1 Load
```{r}
# Get data
user <- all_data |> distinct( User_original)
user <-  data.frame(User_original = user[!is.na(user$User_original),])
# 3644

# Get all relevant columns
user$User_GBIF <- NA
user$User_rank <- NA
user$User_GBIF_ID <- NA
user$User_GBIF_accepted_name <- NA
user$User_subspecies <- NA
user$User_species <- NA
user$User_genus <- NA
user$User_family<- NA
user$validated <- NA
```


```{r}
# First check against our own database
check <- user[user$User_original %in% names_plantnet$GBIF,]
check$validated <- T
check$User_subspecies <- names_plantnet$GBIF_subspecies[match(check$User_original, names_plantnet$GBIF)]
check$User_species <- names_plantnet$GBIF_species[match(check$User_original, names_plantnet$GBIF)]
check$User_genus <- names_plantnet$GBIF_genus[match(check$User_original, names_plantnet$GBIF)]
check$User_family <- names_plantnet$GBIF_family[match(check$User_original, names_plantnet$GBIF)]
check$User_GBIF_accepted_name <- names_plantnet$GBIF_accepted[match(check$User_original, names_plantnet$GBIF)]
check$User_GBIF_ID <- names_plantnet$GBIF_ID[match(check$User_original, names_plantnet$GBIF)]
check$User_GBIF <- names_plantnet$GBIF[match(check$User_original, names_plantnet$GBIF)]
check$User_rank <- names_plantnet$GBIF_rank[match(check$User_original, names_plantnet$GBIF)]

# Here is a version to compare
user_save <- user
user_save[user_save$User_original %in% names_plantnet$GBIF,] <- check

# User remaining
user <- user_save[is.na(user_save$validated),]
sum(is.na(user_save$validated))
# 1778 remain
```



## 4.2 GBIF
```{r}
# We use GBIF 
# We use the original name to avoid inconsistencies
gbif <- name_backbone_checklist(user$User_original[1])
# subdivide to avoid R crashing
for(i in 1: 10){
  # boundaries
  begin <- 1+ floor(length(user$User_original)/10*(i-1))
  end <- floor(length(user$User_original)/10 * i)
  # run 
  data_gbif <- name_backbone_checklist(user$User_original[begin: end])
  gbif <- bind_rows(gbif, data_gbif)
}
gbif <- gbif[-1,]
gbif_nine <- gbif
```

### Animalia
```{r}
# Animals
gbif_non_plant <- gbif[gbif$kingdom != "Plantae" & !is.na(gbif$usageKey),]

# We use the original name to avoid inconsistencies again, some genera etc are both plants and bees 
gbif_check <- name_backbone_checklist(gbif_non_plant$verbatim_name[1])
# subdivide to avoid R crashing
for(i in 1: 10){
  # boundaries
  begin <- 1+ floor(length(gbif_non_plant$verbatim_name)/10*(i-1))
  end <- floor(length(gbif_non_plant$verbatim_name)/10 * i)
  # run 
  data_gbif <- name_backbone_checklist(gbif_non_plant$verbatim_name[begin: end], kingdom = "Plantae")
  gbif_check <- bind_rows(gbif_check, data_gbif)
}
gbif_check <- gbif_check[-1,]

# Check
check <- gbif_check[!is.na(gbif_check$phylum),]
check <- check[check$kingdom %in% "Plantae",]
check <- check[!grepl("Andrena|Osmia|Bombus|Araneae|Coleoptera|Lasius", check$verbatim_name), ]
check <- check[check$verbatim_name %in% c("Taraxacum sect. Hamata", "Hedera spec.","Pastinaca spec."),]

# Remove the plants here
gbif_non_plant <- gbif_non_plant[!gbif_non_plant$verbatim_name %in% check$verbatim_name,]


# Remove these all
user_save <- user_save[!user_save$User_original %in% gbif_non_plant$verbatim_name,]
# We also remove these from our overall database (997)
nrow(all_data[all_data$User_original %in%  gbif_non_plant$verbatim_name,] )
all_data <- all_data[!all_data$User_original %in%  gbif_non_plant$verbatim_name,] 



# Later we found some more, also remove (20)
user_save <- user_save[!user_save$User_original %in% c("Osmia spec.", "Campanella spec", "Hunter", "Acari indet.", "Halictini indet.", "Sternorrhyncha indet.", 
                                                       "Pisces spec.", "Angler", "Bryophyta indet.", "Pteropsida indet."),]
check <- all_data[all_data$User_original %in%  c("Osmia spec.", "Campanella spec", "Hunter", "Acari indet.", "Halictini indet.", "Sternorrhyncha indet.", 
                                                       "Pisces spec.", "Angler",  "Bryophyta indet.", "Pteropsida indet." ),] 
all_data <- all_data[!all_data$User_original %in% check$User_original,] 


# We will also remove the data which is at a too high level from the dataset here, but these are plants so can be kept in the dataset
user_save <- user_save[!user_save$User_original %in% c("Plantae indet.",  "Pinopsida indet.", "Bambusoideae indet."),]
all_data$User_original[all_data$User_original %in%  c("Plantae indet.",  "Pinopsida indet.", "Bambusoideae indet.")] <- NA
# 3344 user species left
```


### Accepted
```{r}
user <- user_save[is.na(user_save$validated),]
#######
gbif_acc <- gbif[gbif$status == "ACCEPTED" & gbif$matchType == "EXACT" & !gbif$verbatim_name %in% gbif_non_plant$verbatim_name,]


# Create final data
gbif_acc$final <- gbif_acc$subspecies
gbif_acc$final[is.na(gbif_acc$final)] <- gbif_acc$form[is.na(gbif_acc$final)]
gbif_acc$final[is.na(gbif_acc$final)] <- gbif_acc$variety[is.na(gbif_acc$final)]
gbif_acc$final[is.na(gbif_acc$final)] <- gbif_acc$species[is.na(gbif_acc$final)]
gbif_acc$final[is.na(gbif_acc$final)] <- gbif_acc$genus[is.na(gbif_acc$final)]
gbif_acc$final[is.na(gbif_acc$final)] <- gbif_acc$family[is.na(gbif_acc$final)]
# Keys
gbif_acc$final_key <- gbif_acc$subspeciesKey
gbif_acc$final_key[is.na(gbif_acc$final_key)] <- gbif_acc$formKey[is.na(gbif_acc$final_key)]
gbif_acc$final_key[is.na(gbif_acc$final_key)] <- gbif_acc$varietyKey[is.na(gbif_acc$final_key)]
gbif_acc$final_key[is.na(gbif_acc$final_key)] <- gbif_acc$speciesKey[is.na(gbif_acc$final_key)]
gbif_acc$final_key[is.na(gbif_acc$final_key)] <- gbif_acc$genusKey[is.na(gbif_acc$final_key)]
gbif_acc$final_key[is.na(gbif_acc$final_key)] <- gbif_acc$familyKey[is.na(gbif_acc$final_key)]


#######
# Check accepted
# Check whether they are the same as the verbatim names
gbif_acc$verbatim_name_new <- gsub("subsp. ", "", gbif_acc$verbatim_name)
gbif_acc$verbatim_name_new <- gsub("var. ", "", gbif_acc$verbatim_name_new)
gbif_acc$validated <- NA
# Reduce dataset to those observations for which there is a difference between the final and accepted name
check <- gbif_acc[!gbif_acc$verbatim_name_new == gbif_acc$final,]
# This is due to problems in terms of extra information originally given by the user


######
# We include this in the rank info
gbif_acc$rank_again <- NA
# Cultivars
gbif_acc$rank_again[grepl("(cultivar)", gbif_acc$verbatim_name_new)] <- "cultivar"
gbif_acc$rank_again[grepl("'[^']+'", gbif_acc$verbatim_name_new)] <- "cultivar"
gbif_acc$rank_again[grepl("auct. hort", gbif_acc$verbatim_name_new)] <- "cultivar"
# Sector data
gbif_acc$rank_again[grepl("sect.", gbif_acc$verbatim_name_new)] <- "sector"
# Forma data
gbif_acc$rank_again[grepl("f. ", gbif_acc$verbatim_name_new)] <- "form"
# Aggregated species
gbif_acc$rank_again[grepl("\\+", gbif_acc$verbatim_name_new)] <- "aggregate"
# Hybrids
gbif_acc$rank_again[grepl(" x ", gbif_acc$verbatim_name_new)] <- "hybrid"
# Subgenera
gbif_acc$rank_again[grepl("subg. ", gbif_acc$verbatim_name_new)] <- "genus"
# Uncertainties (just accepted)
gbif_acc$rank_again[grepl("s\\.l\\.", gbif_acc$verbatim_name_new)] <- "species"
gbif_acc$rank_again[grepl("s\\.s\\.", gbif_acc$verbatim_name_new)] <- "species"

# Some are remaining and will be resolved manually
gbif_acc$rank_again[gbif_acc$verbatim_name %in% "Agave americana var. expansa"] <- "variety"
gbif_acc$verbatim_name_new[gbif_acc$verbatim_name %in% "Agave americana var. expansa"] <- "Agave americana expansa"



#####
# Create subspecies and variety combined data (these are all together within subspecies column)
gbif_acc$smallest <- gbif_acc$subspecies
gbif_acc$smallest[is.na(gbif_acc$smallest)] <- gbif_acc$form[is.na(gbif_acc$smallest)]
gbif_acc$smallest[is.na(gbif_acc$smallest)] <- gbif_acc$variety[is.na(gbif_acc$smallest)]
# Keys
gbif_acc$smallest_key <- gbif_acc$subspeciesKey
gbif_acc$smallest_key[is.na(gbif_acc$smallest_key)] <- gbif_acc$formKey[is.na(gbif_acc$smallest_key)]
gbif_acc$smallest_key[is.na(gbif_acc$smallest_key)] <- gbif_acc$varietyKey[is.na(gbif_acc$smallest_key)]

# Assign changed ranks
user$User_rank <- gbif_acc$rank_again[match(user$User_original, gbif_acc$verbatim_name)]
# Assign Subspecies
user$User_subspecies <- gbif_acc$smallest[match(user$User_original, gbif_acc$verbatim_name)]
user$User_GBIF_ID <- gbif_acc$smallest_key[match(user$User_original, gbif_acc$verbatim_name)]
user$User_rank[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- "subspecies"
# Assign species
user$User_species <- gbif_acc$species[match(user$User_original, gbif_acc$verbatim_name)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_acc$speciesKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_acc$verbatim_name)]
user$User_rank[!is.na(user$User_species) & is.na(user$User_rank)] <- "species"
# Assign genus
user$User_genus <- gbif_acc$genus[match(user$User_original, gbif_acc$verbatim_name)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_acc$genusKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_acc$verbatim_name)]
# Assign family
user$User_family <- gbif_acc$family[match(user$User_original, gbif_acc$verbatim_name)]
# Assign final names
user$User_GBIF <- gbif_acc$final[match(user$User_original, gbif_acc$verbatim_name)]
user$User_GBIF_accepted_name <- gbif_acc$scientificName[match(user$User_original, gbif_acc$verbatim_name)]
user$validated[!is.na(user$User_GBIF)] <- T

# Assign
user_save[is.na(user_save$validated),] <- user
# Remaining
sum(is.na(user$validated))
# 1127
```


### Higher
```{r}
######
# Get smaller dataset
user <- user_save[is.na(user_save$validated),]
# Higher ranks
gbif_acc <- gbif[gbif$status == "ACCEPTED" & gbif$matchType == "HIGHERRANK",]

# Get all the ones that are genera
# Only get the genera
gbif_gen <- gbif_acc[grepl(" spec\\.",gbif_acc$verbatim_name), ]

# Check which are equal
check <- gbif_gen[gbif_gen$genus == gsub(" spec\\.","", gbif_gen$verbatim_name) & !is.na(gbif_gen$genus),]

# These may already be assigned
user$User_genus <- check$genus[match(user$User_original, check$verbatim_name)]
user$User_GBIF_ID <- check$genusKey[match(user$User_original, check$verbatim_name)]
user$User_family <- check$family[match(user$User_original, check$verbatim_name)]
user$User_GBIF_accepted_name <- check$scientificName[match(user$User_original, check$verbatim_name)]
user$User_GBIF <- check$genus[match(user$User_original, check$verbatim_name)]
user$User_rank[!is.na(user$User_genus)] <- "genus"
user$validated[!is.na(user$User_genus)] <- T

# Assign
user_save[is.na(user_save$validated),] <- user
# Remaining
sum(is.na(user$validated))
# 692
```


### Synonym
```{r}
######
# Get smaller dataset again
user <- user_save[is.na(user_save$validated),]


######
# Synonyms
gbif_syn <- gbif[gbif$status %in% "SYNONYM" & gbif$matchType == "EXACT",]
gbif_syn <- gbif_syn[!gbif_syn %in% user_save$User_original[!is.na(user_save$validated)]]


# Create final data (subspecies, variety and forma)
gbif_syn$final <- gbif_syn$subspecies
gbif_syn$final[is.na(gbif_syn$final)] <- gbif_syn$form[is.na(gbif_syn$final)]
gbif_syn$final[is.na(gbif_syn$final)] <- gbif_syn$variety[is.na(gbif_syn$final)]
# Create final keys
gbif_syn$usageKey[!is.na(gbif_syn$acceptedUsageKey)] <- gbif_syn$acceptedUsageKey[!is.na(gbif_syn$acceptedUsageKey)]
gbif_syn$scientificName[!is.na(gbif_syn$acceptedScientificName)] <- gbif_syn$acceptedScientificName[!is.na(gbif_syn$acceptedScientificName)]


# Again change some ranks
# We include this in the rank info
gbif_syn$rank_again <- NA
# Cultivars
gbif_syn$rank_again[grepl("(cultivar)", gbif_syn$verbatim_name)] <- "cultivar"
gbif_syn$rank_again[grepl("'[^']+'", gbif_syn$verbatim_name)] <- "cultivar"
gbif_syn$rank_again[grepl("auct. hort", gbif_syn$verbatim_name)] <- "cultivar"
# Sector data
gbif_syn$rank_again[grepl("sect.", gbif_syn$verbatim_name)] <- "sector"
# Forma data
gbif_syn$rank_again[grepl("f. ", gbif_syn$verbatim_name)] <- "form"
# Aggregated species
gbif_syn$rank_again[grepl("\\+", gbif_syn$verbatim_name)] <- "aggregate"
# Hybrids
gbif_syn$rank_again[grepl(" x ", gbif_syn$verbatim_name)] <- "hybrid"
# Subgenera
gbif_syn$rank_again[grepl("subg. ", gbif_syn$verbatim_name)] <- "genus"
# Uncertainties (just accepted)
gbif_syn$rank_again[grepl("s\\.l\\.", gbif_syn$verbatim_name)] <- "species"
gbif_syn$rank_again[grepl("s\\.s\\.", gbif_syn$verbatim_name)] <- "species"


# Assign changed ranks
user$User_rank <- gbif_syn$rank_again[match(user$User_original, gbif_syn$verbatim_name)]
# Assign Subspecies
user$User_subspecies <- gbif_syn$final[match(user$User_original, gbif_syn$verbatim_name)]
user$User_GBIF_ID <- gbif_syn$usageKey[match(user$User_original, gbif_syn$verbatim_name)]
user$User_rank[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- "subspecies"
# Assign species
user$User_species <- gbif_syn$species[match(user$User_original, gbif_syn$verbatim_name)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_syn$usageKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_syn$verbatim_name)]
user$User_rank[!is.na(user$User_species) & is.na(user$User_rank)] <- "species"
# Assign genus
user$User_genus <- gbif_syn$genus[match(user$User_original, gbif_syn$verbatim_name)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_syn$usageKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_syn$verbatim_name)]
# Assign family
user$User_family <- gbif_syn$family[match(user$User_original, gbif_syn$verbatim_name)]
# Assign final names
gbif_syn$final[is.na(gbif_syn$final)] <- gbif_syn$species[is.na(gbif_syn$final)]
gbif_syn$final[is.na(gbif_syn$final)] <- gbif_syn$genus[is.na(gbif_syn$final)]
user$User_GBIF <- gbif_syn$final[match(user$User_original, gbif_syn$verbatim_name)]
user$User_GBIF_accepted_name <- gbif_syn$scientificName[match(user$User_original, gbif_syn$verbatim_name)]
user$validated[!is.na(user$User_GBIF)] <- T


# Assign
user_save[is.na(user_save$validated),] <- user
sum(is.na(user_save$validated))
# 427 remain
```


## 4.3 GBIFv2
```{r}
# Remaining
user <- user_save[is.na(user_save$validated),] 

# Many are genera with spp. as an indicator
# Remove spp. and check again against gbif
user$new_name <- gsub(" spec\\..*$", "", user$User_original)
user$new_name <- gsub("\\s*\\([^)]*\\)", "", user$new_name)
user$new_name <- gsub(" agg\\..*$", "", user$new_name)
user$new_name <- gsub(" indet\\..*$", "", user$new_name)
user$new_name <- gsub(" s\\.l\\.", "", user$new_name)
user$new_name <- gsub(" s\\.s\\.", "", user$new_name)
user$new_name <- gsub(" '[^']+'", "", user$new_name)


# Check gbif again
gbif <-  name_backbone_checklist(user$new_name[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(user$new_name)/2*(i-1))
  end <- floor(length(user$new_name)/2 * i)
  # run 
  data <- name_backbone_checklist(user$new_name[begin: end], kingdom = "Plantae")
  gbif <- bind_rows(gbif, data)
}
gbif <- gbif[-1,]
gbif_ten <- gbif
```


### Accepted
```{r}
# Get accepted and exact
gbif_acc <- gbif[gbif$status== "ACCEPTED" & gbif$matchType == "EXACT",]

# Get all names
gbif_acc$final <- gbif_acc$species
gbif_acc$final[is.na(gbif_acc$final)] <- gbif_acc$genus[is.na(gbif_acc$final)]
gbif_acc$final[is.na(gbif_acc$final)] <- gbif_acc$family[is.na(gbif_acc$final)]


# Check how well they correspond
gbif_acc$verbatim_name_new <- gsub(" x ", " ", gbif_acc$verbatim_name)
check <- gbif_acc[!gbif_acc$verbatim_name_new == gbif_acc$final & !is.na(gbif_acc$verbatim_name),]
gbif_acc$rank_again <- NA
gbif_acc$rank_again[grepl(" x ", gbif_acc$verbatim_name)] <- "hybrid"
# Looks fine, all assign


#####
# Assign changed ranks
user$User_rank <- gbif_acc$rank_again[match(user$new_name, gbif_acc$verbatim_name)]
# Assign species
user$User_species <- gbif_acc$species[match(user$new_name, gbif_acc$verbatim_name)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_acc$speciesKey[match(user$new_name[is.na(user$User_GBIF_ID)] , gbif_acc$verbatim_name)]
user$User_rank[!is.na(user$User_species) & is.na(user$User_rank)] <- "species"
# Assign genus
user$User_genus <- gbif_acc$genus[match(user$new_name, gbif_acc$verbatim_name)]
user$User_rank[!is.na(user$User_genus) & is.na(user$User_rank)] <- "genus"
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_acc$genusKey[match(user$new_name[is.na(user$User_GBIF_ID)] , gbif_acc$verbatim_name)]
# Assign family
user$User_family <- gbif_acc$family[match(user$new_name, gbif_acc$verbatim_name)]
user$User_rank[!is.na(user$User_family) & is.na(user$User_rank)] <- "family"
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_acc$familyKey[match(user$new_name[is.na(user$User_GBIF_ID)] , gbif_acc$verbatim_name)]
# Assign final names
user$User_GBIF <- gbif_acc$final[match(user$new_name, gbif_acc$verbatim_name)]
user$User_GBIF_accepted_name <- gbif_acc$scientificName[match(user$new_name, gbif_acc$verbatim_name)]
user$validated[!is.na(user$User_GBIF)] <- T


# Assign
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 182 left
```


### Variant
```{r}
# Remaining
user <- user_save[is.na(user_save$validated),] 

# Remove spp. and check again against gbif
user$new_name <- gsub(" spec\\..*$", "", user$User_original)
user$new_name <- gsub("\\s*\\([^)]*\\)", "", user$new_name)
user$new_name <- gsub(" agg\\..*$", "", user$new_name)
user$new_name <- gsub(" indet\\..*$", "", user$new_name)
user$new_name <- gsub(" s\\.l\\.", "", user$new_name)
user$new_name <- gsub(" s\\.s\\.", "", user$new_name)
user$new_name <- gsub(" '[^']+'", "", user$new_name)

# Get all variants
gbif_var <- gbif[gbif$status %in% c("PROVISIONALLY_ACCEPTED","ACCEPTED") & gbif$matchType %in% c("EXACT", "VARIANT"),]
gbif_var <- gbif_var[gbif_var$verbatim_name %in% user$new_name,]

# Here are some that have to be looked at
change <- c("Veronica sect. Pseudolysimachium", "Eupatorieae","Heliantheae", "Plantae", "Bryophyta", "Pinopsida")
gbif_var <- gbif_var[!gbif_var$verbatim_name %in% change,]


#####
# Assign Subspecies
user$User_subspecies <- gbif_var$subspecies[match(user$User_original, gbif_var$verbatim_name)]
user$User_GBIF_ID <- gbif_var$usageKey[match(user$User_original, gbif_var$verbatim_name)]
user$User_rank[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- "subspecies"
# Assign species
user$User_species <- gbif_var$species[match(user$new_name, gbif_var$verbatim_name)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_var$speciesKey[match(user$new_name[is.na(user$User_GBIF_ID)] , gbif_var$verbatim_name)]
user$User_rank[!is.na(user$User_species) & is.na(user$User_rank)] <- "species"
# Assign genus
user$User_genus <- gbif_var$genus[match(user$new_name, gbif_var$verbatim_name)]
user$User_rank[!is.na(user$User_genus) & is.na(user$User_rank)] <- "genus"
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_var$genusKey[match(user$new_name[is.na(user$User_GBIF_ID)] , gbif_var$verbatim_name)]
# Assign family
user$User_family <- gbif_var$family[match(user$new_name, gbif_var$verbatim_name)]
user$User_rank[!is.na(user$User_family) & is.na(user$User_rank)] <- "family"
# Assign final names
user$User_GBIF <- gbif_var$canonicalName[match(user$new_name, gbif_var$verbatim_name)]
user$User_GBIF_accepted_name <- gbif_var$scientificName[match(user$new_name, gbif_var$verbatim_name)]
user$validated[!is.na(user$User_GBIF)] <- T


# Assign
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 168 remaining
```


### Aggregates
```{r}
# User again
user <- user[is.na(user$validated),]

# We will now only look at the aggregates
agg <- user[grepl("\\s*\\+\\s*", user$User_original) ,]
# We remove one, all the rest have the same genus
agg <- agg[!agg$User_original %in% "Tripleurospermum maritimum + Matricaria chamomilla",]
# Get the genera
agg$User_genus <- sub("^(\\S+).*", "\\1", agg$User_original)

# We will have to look whether they exist and what their ID is
# Check gbif again
gbif_gen <-  name_backbone_checklist(agg$User_genus[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(agg$User_genus)/2*(i-1))
  end <- floor(length(agg$User_genus)/2 * i)
  # run 
  data <- name_backbone_checklist(agg$User_genus[begin: end], kingdom = "Plantae")
  gbif_gen <- bind_rows(gbif_gen, data)
}
gbif_gen <- gbif_gen[-1,]

# Assign
agg$User_GBIF_ID <- gbif_gen$usageKey[match(agg$User_genus, gbif_gen$verbatim_name)]
agg$User_GBIF_accepted_name <- gbif_gen$scientificName[match(agg$User_genus, gbif_gen$verbatim_name)]
agg$User_family <- gbif_gen$family[match(agg$User_genus, gbif_gen$verbatim_name)]
agg$User_GBIF <- gbif_gen$genus[match(agg$User_genus, gbif_gen$verbatim_name)]
agg$User_rank <- "aggregate"
agg$validated <-T

# Assign
user[user$User_original %in% agg$User_original,] <- agg
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 130 remaining
```

### Higher
```{r}
# User again
user <- user[is.na(user$validated),]

# Check how they look in gbif
gbif_remaining <- gbif[gbif$verbatim_name %in% user$new_name,]
# Higher ranks
gbif_gen <- gbif_remaining[gbif_remaining$status == "ACCEPTED" & gbif_remaining$matchType == "HIGHERRANK",]

# Get all the ones that are genera
check <- gbif_gen[gbif_gen$genus == gbif_gen$verbatim_name & !is.na(gbif_gen$genus),]

# These may already be assigned
user$User_genus <- check$genus[match(user$new_name, check$verbatim_name)]
user$User_GBIF_ID <- check$genusKey[match(user$new_name, check$verbatim_name)]
user$User_family <- check$family[match(user$new_name, check$verbatim_name)]
user$User_GBIF_accepted_name <- check$scientificName[match(user$new_name, check$verbatim_name)]
user$User_GBIF <- check$genus[match(user$new_name, check$verbatim_name)]
user$User_rank[!is.na(user$User_genus)] <- "genus"
user$validated[!is.na(user$User_genus)] <- T

# Assign
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 110 remaining
```


### Sector
```{r}
# Many remaining are sector, we treat them as we treated aggregates
# We will now only look at the aggregates
user <- user[is.na(user$validated),]
sec <- user[grepl("sect.", user$User_original) ,]
# Get the genera
sec$User_genus <- sub("^(\\S+).*", "\\1", sec$User_original)

# We will have to look whether they exist and what their ID is
# Check gbif again
gbif_gen <-  name_backbone_checklist(sec$User_genus[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(sec$User_genus)/2*(i-1))
  end <- floor(length(sec$User_genus)/2 * i)
  # run 
  data <- name_backbone_checklist(sec$User_genus[begin: end], kingdom = "Plantae")
  gbif_gen <- bind_rows(gbif_gen, data)
}
gbif_gen <- gbif_gen[-1,]


# Assign
sec$User_GBIF_ID <- gbif_gen$usageKey[match(sec$User_genus, gbif_gen$verbatim_name)]
sec$User_GBIF_accepted_name <- gbif_gen$scientificName[match(sec$User_genus, gbif_gen$verbatim_name)]
sec$User_family <- gbif_gen$family[match(sec$User_genus, gbif_gen$verbatim_name)]
sec$User_GBIF <- gbif_gen$genus[match(sec$User_genus, gbif_gen$verbatim_name)]
sec$User_rank <- "sector"
sec$validated <-T

# Taraxacum keeps being anoying
sec$User_GBIF_accepted_name[sec$User_genus %in% "Taraxacum"] <- "Taraxacum Weber"
sec$User_GBIF_ID[sec$User_genus %in% "Taraxacum"] <- 7787708
sec$User_GBIF[sec$User_genus %in% "Taraxacum"] <- "Taraxacum"

# Assign
user[user$User_original %in% sec$User_original,] <- sec
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 100 remaining

# Save user save 
user_save_save <- user_save
```


### Tribes
```{r}
# User again
user <- user[is.na(user$validated),]

# Some remaining are tribes from the Asteraceae family
tribes_subfamilies <- c("Astereae spec.", "Senecieae spec.", "Eupatorieae spec.",  "Cardueae spec.",  "Anthemideae spec.", "Heliantheae spec.", 
                        "Calendulaea spec.",  "Cichorieae spec.", "Carduoideae indet.")
user$User_family[user$User_original %in% tribes_subfamilies] <- "Asteraceae"
user$User_rank[user$User_original %in% tribes_subfamilies] <- "tribe"
user$User_rank[user$User_original %in% c("Carduoideae indet.")] <- "subfamily"
user$User_GBIF[user$User_original %in% tribes_subfamilies] <- gsub(" spec.", "", user$User_original[user$User_original %in% tribes_subfamilies] )
user$User_GBIF_ID[user$User_original %in% tribes_subfamilies] <- 3065
user$User_GBIF_accepted_name[user$User_original %in% tribes_subfamilies] <- "Asteraceae"
user$validated[user$User_original %in% tribes_subfamilies] <- T

# Assign
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 91 remaining
```


### Old
```{r}
# User again
user <- user[is.na(user$validated),]

# Check 
check <- user[user$User_original %in% names_plantnet$Name,]
check$User_subspecies <- names_plantnet$GBIF_subspecies[match(check$User_original, names_plantnet$Name)]
check$User_species <- names_plantnet$GBIF_species[match(check$User_original, names_plantnet$Name)]
check$User_genus <- names_plantnet$GBIF_genus[match(check$User_original, names_plantnet$Name)]
check$User_family <- names_plantnet$GBIF_family[match(check$User_original, names_plantnet$Name)]
check$User_GBIF_accepted_name <- names_plantnet$GBIF_accepted[match(check$User_original, names_plantnet$Name)]
check$User_GBIF_ID <- names_plantnet$GBIF_ID[match(check$User_original, names_plantnet$Name)]
check$User_GBIF <- names_plantnet$GBIF[match(check$User_original, names_plantnet$Name)]
check$User_rank <- names_plantnet$GBIF_rank[match(check$User_original, names_plantnet$Name)]
check$validated <- T

# Assign
user[user$User_original %in% names_plantnet$Name,] <- check
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 76 remaining
```


### Verbose
```{r}
# User again
user <- user[is.na(user$validated),]

# Verbose function
# We will have to look whether they exist and what their ID is
verbose <-  as.data.frame(name_backbone_verbose(user$User_original[1])[2])[1,]
for(i in 2: nrow(user)){ 
  data <-  as.data.frame(name_backbone_verbose(user$User_original[i])[2])[1,]
  verbose <- bind_rows(verbose, data)
}

# Get all plants
acc_verbose <- verbose[verbose$alternatives.kingdom %in% "Plantae",]

# Assign accepted
acc_verbose$alternatives.usageKey[!is.na(acc_verbose$alternatives.acceptedUsageKey)] <-
  acc_verbose$alternatives.acceptedUsageKey[!is.na(acc_verbose$alternatives.acceptedUsageKey)]
acc_verbose$alternatives.scientificName[!is.na(acc_verbose$alternatives.acceptedScientificName)] <-
  acc_verbose$alternatives.acceptedScientificName[!is.na(acc_verbose$alternatives.acceptedScientificName)]

# Check which are incorrect 
change <- data.frame(old = c("Cardaminopsis spec.", "Cardaminopsis spec.", "Eupatorium rugosum", 
                            "Galeobdolon spec.", "Geranium macrorrhizum subsp. macrorrhizum", "Inula conyzae", 
                            "Lavatera spec.", "Lavatera thuringiaca", "Lychnis spec.", "Lycopersicon esculentum",
                            "Mimulus guttatus", "Oenothera hybrid s.l.", "Paeonia hybrida", "Perovskia spec.",
                            "Potentilla rupestris", "Rosmarinus spec.", "Rubus genevieri", "Sorbus intermedia",
                            "Trifolium speciosum"),
                    new = c("Clinopodium L.", "Arabidopsis (DC.) Heynh.", 
                            "Ageratina altissima (L.) R.M.King & H.Rob.", "Lamium L.",
                            "Geranium dalmaticum (Beck) Rech. f.", 
                            "Pentanema squarrosum (L.) D.Gut.Larr., Santos-Vicente, Anderb., E.Rico & M.M.Mart.Ort.",
                            "Malva L.", "Malva thuringiaca subsp. thuringiaca", "Silene L.",
                            "Solanum lycopersicum L.", "Erythranthe guttata (DC.) G.L.Nesom", 
                            "Oenothera tetragona Roth", "Paeonia tenuifolia L.", "Salvia L.", 
                            "Drymocallis rupestris (L.) Soják", "Salvia L.", "Rubus bracteatus Boreau", 
                            "Hedlundia intermedia (Ehrh.) Mosyakin, Fedor. & McNeill", 
                            "Trifolium grandiflorum Schreb."))

# Remove these already
acc_verbose <- acc_verbose[!acc_verbose$alternatives.verbatim_name %in% change$old,]

# Assign Subspecies
user$User_subspecies <- acc_verbose$alternatives.subspecies[match(user$User_original, acc_verbose$alternatives.verbatim_name)]
user$User_GBIF_ID <- acc_verbose$alternatives.usageKey[match(user$User_original, acc_verbose$alternatives.verbatim_name)]
user$User_GBIF[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- user$User_subspecies[!is.na(user$User_subspecies)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- "subspecies"
# Assign species
user$User_species <- acc_verbose$alternatives.species[match(user$User_original, acc_verbose$alternatives.verbatim_name)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- acc_verbose$alternatives.usageKey[match(user$User_original[is.na(user$User_GBIF_ID)] ,
                                                                                       acc_verbose$alternatives.verbatim_name)]
user$User_GBIF[!is.na(user$User_species)& is.na(user$User_rank)] <- user$User_species[!is.na(user$User_species)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_species) & is.na(user$User_rank)] <- "species"
# Assign genus
user$User_genus <- acc_verbose$alternatives.genus[match(user$User_original, acc_verbose$alternatives.verbatim_name)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- acc_verbose$alternatives.usageKey[match(user$User_original[is.na(user$User_GBIF_ID)] , acc_verbose$alternatives.verbatim_name)]
user$User_GBIF[!is.na(user$User_genus)& is.na(user$User_rank)] <- user$User_genus[!is.na(user$User_genus)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_genus) & is.na(user$User_rank)] <- "genus"
# Assign family
user$User_family <- acc_verbose$alternatives.family[match(user$User_original, acc_verbose$alternatives.verbatim_name)]
# Assign final names
user$User_GBIF_accepted_name <- acc_verbose$alternatives.scientificName[match(user$User_original, acc_verbose$alternatives.verbatim_name)]
user$validated[!is.na(user$User_GBIF)] <- T

# Assign
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 41


#####
# User again
user <- user[is.na(user$validated),]
gbif_change <- name_backbone_checklist(change$new[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(change$new)/2*(i-1))
  end <- floor(length(change$new)/2 * i)
  # run 
  data <- name_backbone_checklist(change$new[begin: end], kingdom = "Plantae")
  gbif_change <- bind_rows(gbif_change, data)
}
gbif_change <- gbif_change[-1,]

# One is still incorrect
gbif_change <- gbif_change[!gbif_change$verbatim_name %in% c("Hedlundia intermedia (Ehrh.) Mosyakin, Fedor. & McNeill"),]
gbif_change$old <- change$old[match(gbif_change$verbatim_name, change$new)]


# Assign Subspecies
user$User_subspecies <- gbif_change$subspecies[match(user$User_original, gbif_change$old)]
user$User_GBIF_ID <- gbif_change$subspeciesKey[match(user$User_original, gbif_change$old)]
user$User_GBIF[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- user$User_subspecies[!is.na(user$User_subspecies)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- "subspecies"
# Assign species
user$User_species <- gbif_change$species[match(user$User_original, gbif_change$old)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_change$speciesKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_change$old)]
user$User_GBIF[!is.na(user$User_species)& is.na(user$User_rank)] <- user$User_species[!is.na(user$User_species)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_species) & is.na(user$User_rank)] <- "species"
# Assign genus
user$User_genus <- gbif_change$genus[match(user$User_original,gbif_change$old)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_change$genusKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_change$old)]
user$User_GBIF[!is.na(user$User_genus)& is.na(user$User_rank)] <- user$User_genus[!is.na(user$User_genus)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_genus) & is.na(user$User_rank)] <- "genus"
# Assign family
user$User_family <- gbif_change$family[match(user$User_original,gbif_change$old)]
# Assign final names
user$User_GBIF_accepted_name <- gbif_change$scientificName[match(user$User_original, gbif_change$old)]
user$validated[!is.na(user$User_GBIF)] <- T

# Assign
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
# 25 remaining
```


### Remaining
```{r}
# The last ones I will just do manually
user <- user_save[is.na(user_save$validated),] 

# Manual changes against GBIF
change <- data.frame(old = user$User_original,
                     new = c("Salix gmelinii Pall.", "Veronica L.", "Taraxacum erythrospermum Andrz. ex Besser",
                             "Clinopodium calamintha (L.) Kuntze", "Viola tricolor L.", "Salix cinerea subsp. cinerea", "Salvia L.", "Aconitum × cammarum L.", 
                             "Petunia × atkinsiana D.Don ex Loudon", "Asteraceae", "Salvia × lavandulacea (de Noé) P.P.Ferrer", "Rhinanthus minor subsp. minor", 
                             "Salix caprea x udensis", "Symphytum officinale subsp. officinale", "Allium paradoxum (M.Bieb.) G.Don","Acanthus mollis subsp. mollis" ,
                             "Vaccinium angustifolium x corymbosum", 
                             "Hedlundia intermedia (Ehrh.) Mosyakin, Fedor. & McNeill", "Petrosedum rupestre (L.) P.V.Heath", "Cota tinctoria subsp. tinctoria", 
                             "Origanum vulgare subsp. virens (Hoffmanns. & Link) Bonnier & Layens", "Symphoricarpos Dill. ex Juss.", "Salix udensis x viminalis", 
                             "Malus domestica (Suckow) Borkh.", "Cosmos Cav."))


# Try again gbif, ID's would be good
gbif_change <- name_backbone_checklist(change$new[1])
for(i in 1: 2){
  # boundaries
  begin <- 1 + floor(length(change$new)/2*(i-1))
  end <- floor(length(change$new)/2 * i)
  # run 
  data <- name_backbone_checklist(change$new[begin: end], kingdom = "Plantae")
  gbif_change <- bind_rows(gbif_change, data)
}
gbif_change <- gbif_change[-1,]

# Remove the higher ranks
gbif_change <- gbif_change[gbif_change$matchType %in% "EXACT",]
gbif_change$old <- change$old[match(gbif_change$verbatim_name, change$new)]

# Assign Subspecies
user$User_subspecies <- gbif_change$subspecies[match(user$User_original, gbif_change$old)]
user$User_GBIF_ID <- gbif_change$subspeciesKey[match(user$User_original, gbif_change$old)]
user$User_GBIF[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- user$User_subspecies[!is.na(user$User_subspecies)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_subspecies)& is.na(user$User_rank)] <- "subspecies"
# Assign species
user$User_species <- gbif_change$species[match(user$User_original, gbif_change$old)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_change$speciesKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_change$old)]
user$User_GBIF[!is.na(user$User_species)& is.na(user$User_rank)] <- user$User_species[!is.na(user$User_species)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_species) & is.na(user$User_rank)] <- "species"
# Assign genus
user$User_genus <- gbif_change$genus[match(user$User_original,gbif_change$old)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_change$genusKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_change$old)]
user$User_GBIF[!is.na(user$User_genus)& is.na(user$User_rank)] <- user$User_genus[!is.na(user$User_genus)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_genus) & is.na(user$User_rank)] <- "genus"
# Assign family
user$User_family <- gbif_change$family[match(user$User_original,gbif_change$old)]
user$User_GBIF_ID[is.na(user$User_GBIF_ID)] <- gbif_change$familyKey[match(user$User_original[is.na(user$User_GBIF_ID)] , gbif_change$old)]
user$User_GBIF[!is.na(user$User_family)& is.na(user$User_rank)] <- user$User_family[!is.na(user$User_family)& is.na(user$User_rank)]
user$User_rank[!is.na(user$User_family) & is.na(user$User_rank)] <- "family"
# Assign final names
user$User_GBIF_accepted_name <- gbif_change$scientificName[match(user$User_original, gbif_change$old)]
user$validated[!is.na(user$User_GBIF)] <- T

# Assign
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))


# Last ones totally manually
user <- user_save[is.na(user_save$validated),] 
change <- data.frame(old = user$User_original, 
                     subspecies = c("Salix cinerea cinerea","Symphytum officinale officinale" , "Acanthus mollis mollis", NA, NA),
                     species = c("Salix cinerea","Symphytum officinale", "Acanthus mollis", "Vaccinium angustifolium x corymbosum", "Hedlundia intermedia"),
                     genus = c("Salix", "Symphytum", "Acanthus", "Vaccinium","Hedlundia"),
                     family = c("Salicaceae", "Boraginaceae", "Acanthaceae", "Ericaceae", "Rosaceae"),
                     accepted = c("Salix cinerea subsp. cinerea", "Symphytum officinale subsp. officinale", "Acanthus mollis subsp. mollis", NA,
                                  "Hedlundia intermedia (Ehrh.) Mosyakin, Fedor. & McNeill"),
                     rank = c("subspecies","subspecies", "subspecies", "hybrid", "species"))

# Assign
user$User_subspecies <- change$subspecies
user$User_species <- change$species
user$User_genus <- change$genus
user$User_family <- change$ family
user$User_rank <- change$rank
user$User_GBIF_accepted_name <- change$accepted
user$User_GBIF <- change$subspecies
user$User_GBIF[is.na(user$User_GBIF)] <- change$species[is.na(user$User_GBIF)]
user$validated <- T

# Assign
user_save[is.na(user_save$validated),] <- user[, 1:10]
sum(is.na(user_save$validated))
```



## 4.4 Check
### Duplicates
```{r}
# Data
user <- user_save

########user_save######
# Duplicates in family
dup <- user |> group_by(User_genus, User_family) |> summarise(n = n())
dup <- dup[duplicated(dup$User_genus) | duplicated(dup$User_genus, fromLast = T),]
dup <- dup[!is.na(dup$User_genus),]
# Assign
user$User_family[user$User_genus %in% dup$User_genus] <- "Araliaceae"


#######
# Duplicates in genus
dup <- user |> group_by(User_species, User_genus, User_family) |> summarise(n = n())
dup <- dup[duplicated(dup$User_species) | duplicated(dup$User_species, fromLast = T),]
# These are all NA species so correct

#######
# Duplicates in species
dup <-  user |> group_by(User_subspecies, User_species, User_genus, User_family) |> summarise(n = n())
dup <- dup[duplicated(dup$User_subspecies) | duplicated(dup$User_subspecies, fromLast = T),]
dup <- dup[!is.na(dup$User_subspecies),]
# These are all correct!



#######
# Duplicates in rank
dup <- user |> group_by(User_rank, User_subspecies, User_species, User_genus, User_family, User_GBIF) |> summarise(n = n())
dup <- dup[duplicated(dup$User_GBIF) | duplicated(dup$User_GBIF, fromLast = T),]
# These look correct
```


### Missing
```{r}
# Some data was missing
user$User_family[user$User_original %in% "Micrasterias decemdentata"] <- "Desmidiaceae"

# Missing accepted names
mis <- user[is.na(user$User_GBIF_accepted_name),]
# Fine, this one could not be found

# Missing IDs
mis <- user[is.na(user$User_GBIF_ID),]
# Fine, this one could not be found using the function

# Missing genera
mis <- user[is.na(user$User_genus),]

# Missing ranks
mis <- user[is.na(user$User_ranks),]
```


### Ranks Original
```{r}
# We will subdivide between the original data and the final data
user$User_original_rank <- NA
user$User_original_rank[grepl("(cultivar)", user$User_original)] <- "cultivar"
user$User_original_rank[grepl("'[^']+'", user$User_original)] <- "cultivar"
user$User_original_rank[grepl("auct. hort", user$User_original)] <- "cultivar"
# Sector
user$User_original_rank[grepl("sect.", user$User_original)& is.na(user$User_original_rank)] <- "sector"
user$User_original_rank[grepl("subsect.", user$User_original)& is.na(user$User_original_rank)] <- "subsector"
# Form
user$User_original_rank[grepl("f\\.", user$User_original)& is.na(user$User_original_rank)] <- "form"
# Aggregates
user$User_original_rank[grepl("\\+", user$User_original)& is.na(user$User_original_rank)] <- "aggregate"
user$User_original_rank[grepl("gr\\.", user$User_original)& is.na(user$User_original_rank)] <- "aggregate"
user$User_original_rank[grepl(" group", user$User_original)& is.na(user$User_original_rank)] <- "aggregate"
user$User_original_rank[grepl("agg\\.", user$User_original)& is.na(user$User_original_rank)] <- "aggregate"
# Uncertain
user$User_original_rank[grepl("s\\.l\\.", user$User_original)& is.na(user$User_original_rank)] <- "uncertain"
user$User_original_rank[grepl("s\\.s\\.", user$User_original)& is.na(user$User_original_rank)] <- "uncertain"
# Hybrid
user$User_original_rank[grepl(" x ", user$User_original) & is.na(user$User_original_rank)] <- "hybrid"
# Genus
user$User_original_rank[grepl("subg\\.", user$User_original) & is.na(user$User_original_rank)] <- "subgenus"
user$User_original_rank[grepl("spec\\.", user$User_original) & is.na(user$User_original_rank)] <- "genus"
# Subspecies
user$User_original_rank[grepl("subsp\\.", user$User_original) & is.na(user$User_original_rank)] <- "subspecies"
# Variety
user$User_original_rank[grepl("var\\.", user$User_original)] <- "variety"
# family, subfamily (and one genus)
user$User_original_rank[grepl("indet\\.", user$User_original)] <- user$User_rank[grepl("indet\\.", user$User_original)]
# All remaining are species
user$User_original_rank[is.na(user$User_original_rank)] <- "species"
# the tribes were assigned incorrectly
user$User_original_rank[user$User_rank %in% "tribe"] <- "tribe"
user$User_original_rank[user$User_rank %in% "family" & user$User_original_rank %in% "genus"] <- "family"
```


### Ranks GBIF
```{r}
# We will subdivide between the original data and the final data
user$User_gbif_rank <- NA
# Form
user$User_gbif_rank[grepl(" f\\.", user$User_GBIF_accepted_name)& is.na(user$User_gbif_rank)] <- "form"
# Hybrid
user$User_gbif_rank[grepl(" x ", user$User_GBIF_accepted_name) & is.na(user$User_gbif_rank)] <- "hybrid"
user$User_gbif_rank[grepl("×", user$User_GBIF_accepted_name) & is.na(user$User_gbif_rank)] <- "hybrid"
user$User_gbif_rank[grepl(" x ", user$User_GBIF) & is.na(user$User_gbif_rank)] <- "hybrid"
# Subspecies
user$User_gbif_rank[grepl("subsp\\.", user$User_GBIF_accepted_name) & is.na(user$User_gbif_rank)] <- "subspecies"
# Variety
user$User_gbif_rank[grepl("var\\.", user$User_GBIF_accepted_name)] <- "variety"
# Assign the family, subfamily data
user$User_gbif_rank[grepl("indet\\.", user$User_original)] <-  user$User_rank[grepl("indet\\.", user$User_original)]

# Check subspecies
# One species is incorrect
user$User_subspecies[user$User_original %in% "Clinopodium calamintha subsp. spruneri"] <- NA
user$User_species[user$User_original %in% "Clinopodium calamintha subsp. spruneri"] <-  "Clinopodium nepeta"
user$User_GBIF[user$User_original %in% "Clinopodium calamintha subsp. spruneri"] <-  "Clinopodium nepeta"
user$User_GBIF_ID[user$User_original %in% "Clinopodium calamintha subsp. spruneri"] <-  8916040
user$User_GBIF[user$User_original %in% "Clinopodium calamintha subsp. spruneri"] <-  "Clinopodium calamintha (L.) Kuntze"

#Assign species
user$User_gbif_rank[!is.na(user$User_species) & is.na(user$User_gbif_rank)] <- "species"
# Assign genus
user$User_gbif_rank[!is.na(user$User_genus) & is.na(user$User_gbif_rank)] <- "genus"
# Remaining are correct
user$User_gbif_rank[is.na(user$User_gbif_rank)] <- user$User_rank[is.na(user$User_gbif_rank)]

# Assign
user$User_rank <- user$User_gbif_rank
user <- user[, c(1:9, 11)]
```


### Errors
```{r}
#####
# Taraxacum sect. Hamata
# Change in user data
user$User_genus[user$User_original %in% "Taraxacum sect. Hamata"] <- "Taraxacum"
user$User_GBIF[user$User_original %in% "Taraxacum sect. Hamata"] <- "Taraxacum"
user$User_family[user$User_original %in% "Taraxacum sect. Hamata"] <- "Asteraceae"
user$User_GBIF_accepted_name[user$User_original %in% "Taraxacum sect. Hamata"] <- "Taraxacum Weber"
user$User_GBIF_ID[user$User_original %in% "Taraxacum sect. Hamata"] <- 7787708


#####
# Taraxacum sect. Scariosa
# Change in user data
user$User_genus[user$User_original %in% "Taraxacum sect. Scariosa"] <- "Taraxacum"
user$User_GBIF[user$User_original %in% "Taraxacum sect. Scariosa"] <- "Taraxacum"
user$User_family[user$User_original %in% "Taraxacum sect. Scariosa"] <- "Asteraceae"
user$User_GBIF_accepted_name[user$User_original %in% "Taraxacum sect. Scariosa"] <- "Taraxacum Weber"
user$User_GBIF_ID[user$User_original %in% "Taraxacum sect. Scariosa"] <- 7787708

#####
# Ranunculus ficaria
# Change in user data
user$User_subspecies[user$User_original %in% "Ranunculus ficaria"] <- "Ficaria verna verna"
user$User_species[user$User_original %in% "Ranunculus ficaria"] <- "Ficaria verna"
user$User_genus[user$User_original %in% "Ranunculus ficaria"] <- "Ficaria verna"
user$User_GBIF[user$User_original %in% "Ranunculus ficaria"] <- "Ficaria verna verna"
user$User_GBIF_accepted_name[user$User_original %in% "Ranunculus ficaria"] <- "Ficaria verna subsp. verna"
user$User_GBIF_ID[user$User_original %in% "Ranunculus ficaria"] <- 7277276
user$User_rank[user$User_original %in% "Ranunculus ficaria"] <- "subspecies"
```






```{r}
# Save
#write_csv(user, "../Extra/Intermediate/User_names_cleaning_newest_newest.csv")
```



## 4.5 Save
```{r}
# Assign again
all_data$User_subspecies <- user$User_subspecies[match(all_data$User_original, user$User_original)]
all_data$User_species <- user$User_species[match(all_data$User_original, user$User_original)]
all_data$User_genus <- user$User_genus[match(all_data$User_original, user$User_original)]
all_data$User_family <- user$User_family[match(all_data$User_original, user$User_original)]
all_data$Plant_user <- user$User_GBIF[match(all_data$User_original, user$User_original)]
all_data$User_rank <- user$User_rank[match(all_data$User_original, user$User_original)]
all_data$User_GBIF_accepted_name <- user$User_GBIF_accepted_name[match(all_data$User_original, user$User_original)]
all_data$User_GBIF_ID <- user$User_GBIF_ID[match(all_data$User_original, user$User_original)]
all_data$User_original_rank <- user$User_original_rank[match(all_data$User_original, user$User_original)]

#write_csv(all_data, "../Results/Bees_all_observations.csv")
```


# FINAL
## 5.1 Load
```{r}
# Original dataset
pol <- read.csv("../Data/Observation/observation_org_bees.csv")
nat <- read_csv("../Results/iNaturalist_bees_all.csv", show_col_types = FALSE)

# Identifications
pol_plantnet <- read.csv("../Results/Plantnet_identification.csv")
pol_plantnet_iNat <- read.csv("../Results/Plantnet_identification_iNat_all.csv")
```


Combine identifications
```{r}
# Make character
pol_plantnet$ID <- as.character(pol_plantnet$ID)
pol_plantnet <- bind_rows(pol_plantnet, pol_plantnet_iNat)
```


Combine observations
```{r}
## OBSERVATION.ORG ##
# Reduce dataset with relevant columns
pol_data <- pol |> dplyr::select(id, date, time, lat, lng, accuracy, euromed_region, validation.status,
                                 scientific.name, family, species.type, number, sex, life.stage, activity,
                                 related.species, link)

# Add source platform
pol_data$source <- "Observation.org"
pol_data <- pol_data |> relocate(source, .before = id)

# Change names for now
colnames(pol_data) <- c("Platform","Obs_ID","Date","Time","Latitude","Longitude","Coordinate_uncertainty","Euro+Med_region","Observation_quality",
                        "Pol_original","Pol_family_original","Pol_rank_original","Number","Sex","Life_stage","Activity",
                        "User_original","Link")

# Change ID
pol_data$Obs_ID <- as.character(pol_data$Obs_ID)


## iNATURALIST ##
# Assign the link
nat$link <- paste("https://www.inaturalist.org/observations/", nat$observation_uuid, sep= "")

# Get relevant columns
nat_data <- nat |> dplyr::select(observation_uuid, observed_on,  latitude, longitude,positional_accuracy, Country, quality_grade, anomaly_score, 
                                 name, family_inat, link)

# Assign source
nat_data$source <- "iNaturalist.org"
nat_data <- nat_data |> relocate(source, .before = observation_uuid)

colnames(nat_data) <- c("Platform","Obs_ID","Date", "Latitude","Longitude","Coordinate_uncertainty","Euro+Med_region","Observation_quality", "Anomaly_score",
                        "Pol_original","Pol_original_family", "Link")


## COMBINE ##
# Make sure date corresponds
pol_data$Date <- as.Date(pol_data$Date, format = "%Y-%m-%d")
nat_data$Date <- as.Date(nat_data$Date, format = "%Y-%m-%d")

# Combine
all_data <- bind_rows(pol_data, nat_data)
```


## 5.2 Bee
```{r}
# Get bee names
bee_names <- read_csv("../Results/Bee_name_all_last_version.csv", show_col_types = FALSE)

# Assign
all_data$Bee_accepted_name <- bee_names$bee_name[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_accepted_scientific_name <- bee_names$bee_name_scientific[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_subspecies <- bee_names$subspecies[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_species <- bee_names$species[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_genus <- bee_names$genus[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_family <- bee_names$family[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_GBIF_key <- bee_names$key[match(all_data$Pol_original, bee_names$old_name)]
all_data$Bee_rank <- bee_names$rank[match(all_data$Pol_original, bee_names$old_name)]
```




## 5.3 Plantnet
```{r}
# Get plantnet names
names_plantnet <- read_csv("../Extra/Intermediate/Plantnet_names_cleaning_newest_newest.csv", show_col_types = FALSE)

# Assign
pol_plantnet$GBIF_subspecies <- names_plantnet$GBIF_subspecies[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_species <- names_plantnet$GBIF_species[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_genus <- names_plantnet$GBIF_genus[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_family <- names_plantnet$GBIF_family[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_ID_final<- names_plantnet$GBIF_ID[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_accepted_name <- names_plantnet$GBIF_accepted[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_name <- names_plantnet$GBIF[match(pol_plantnet$Name, names_plantnet$Name)]
pol_plantnet$GBIF_rank <- names_plantnet$GBIF_rank[match(pol_plantnet$Name, names_plantnet$Name)]
```


```{r}
# We will assign to the original database
all_data$Plantnet_subspecies <- pol_plantnet$GBIF_subspecies[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_species <- pol_plantnet$GBIF_species[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_genus <- pol_plantnet$GBIF_genus[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_family <- pol_plantnet$GBIF_family[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plant_plantnet <- pol_plantnet$GBIF_name[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_rank <- pol_plantnet$GBIF_rank[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_GBIF_ID <- pol_plantnet$GBIF_ID_final[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_GBIF_accepted_name <- pol_plantnet$GBIF_accepted_name[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_organ <- pol_plantnet$Organ[match(all_data$Obs_ID, pol_plantnet$ID)]
all_data$Plantnet_score <- pol_plantnet$Score[match(all_data$Obs_ID, pol_plantnet$ID)]
```


## 5.4 User
```{r}
# Save
user <- read_csv("../Extra/Intermediate/User_names_cleaning_newest_newest.csv")

# Assign again
all_data$User_subspecies <- user$User_subspecies[match(all_data$User_original, user$User_original)]
all_data$User_species <- user$User_species[match(all_data$User_original, user$User_original)]
all_data$User_genus <- user$User_genus[match(all_data$User_original, user$User_original)]
all_data$User_family <- user$User_family[match(all_data$User_original, user$User_original)]
all_data$Plant_user <- user$User_GBIF[match(all_data$User_original, user$User_original)]
all_data$User_rank <- user$User_rank[match(all_data$User_original, user$User_original)]
all_data$User_GBIF_accepted_name <- user$User_GBIF_accepted_name[match(all_data$User_original, user$User_original)]
all_data$User_GBIF_ID <- user$User_GBIF_ID[match(all_data$User_original, user$User_original)]
all_data$User_original_rank <- user$User_original_rank[match(all_data$User_original, user$User_original)]
```



## 5.5 Errors
### Bees
```{r}
# Read data
# Check Vesitohalictus
check <- all_data[all_data$Bee_accepted_name %in% "Vestitohalictus",]
check$Bee_genus <- "Halictus"
check$Bee_rank <- "subgenus"
all_data[all_data$Bee_accepted_name %in% "Vestitohalictus",]  <- check

# Paramegilla
check <- all_data[all_data$Bee_accepted_name %in% "Paramegilla",]
check$Bee_genus <- "Anthophora"
all_data[all_data$Bee_accepted_name %in% "Paramegilla",]  <- check

# Dialictus
check <- all_data[all_data$Bee_accepted_name %in% "Dialictus",]
check$Bee_genus <- "Lasioglossum"
check$Bee_rank <- "subgenus"
all_data[all_data$Bee_accepted_name %in% "Dialictus",]  <- check

# Monilapis 
check <- all_data[all_data$Bee_accepted_name %in% "Monilapis",]
check$Bee_genus <- "Halictus"
check$Bee_family <- "Halictidae"
check$Bee_rank <- "subgenus"
all_data[all_data$Bee_accepted_name %in% "Monilapis",]  <- check

# Evylaeus
check <- all_data[all_data$Bee_accepted_name %in% "Evylaeus",]
check$Bee_genus <- "Lasioglossum"
check$Bee_rank <- "subgenus"
all_data[all_data$Bee_accepted_name %in% "Evylaeus",]  <- check

# Rhophitoides
check <- all_data[all_data$Bee_accepted_name %in% "Rhophitoides",]
check$Bee_genus <- "Rophites"
check$Bee_rank <- "subgenus"
all_data[all_data$Bee_accepted_name %in% "Rhophitoides",]  <- check

# Cubitalia
check <- all_data[all_data$Bee_accepted_name %in% "Cubitalia",]
check$Bee_genus <- "Eucera"
check$Bee_rank <- "subgenus"
all_data[all_data$Bee_accepted_name %in% "Cubitalia",]  <- check


# Bombus vestalis perezi
check <- all_data[all_data$Pol_original %in% "Bombus vestalis perezi",]
check$Bee_subspecies <- "Bombus vestalis perezi"
check$Bee_species <- "Bombus vestalis"
check$Bee_accepted_name <- "Bombus vestalis perezi"
check$Bee_accepted_scientific_name <- "Bombus vestalis perezi (Schulthess-Rechberg, 1886)"
check$Bee_GBIF_key <- 12269257
check$Bee_rank <- "subspecies"
all_data[all_data$Pol_original %in% "Bombus vestalis perezi",]  <- check


# We did not assign Anthophila but also did not remove them
all_data <- all_data[!all_data$Pol_original %in% "Anthophila",]
all_data <- all_data[!all_data$Pol_original %in% "Sphecodina",]
```


```{r}
# Change some subspecies that are actually species
change <- data.frame(old =  c("Bombus vestalis perezi", "Bombus pascuorum smithianus", "Bombus monticola rondoui", "Bombus pascuorum mniorum", 
                               "Bombus pascuorum melleofacies", "Bombus schrencki schrencki"),
                     new = c("Bombus perezi (Schulthess, 1886)","Bombus pascuorum (Scopoli, 1763)", "Bombus monticola Smith, 1849", "Bombus pascuorum (Scopoli, 1763)",
                             "Bombus pascuorum (Scopoli, 1763)", "Bombus schrencki Morawitz, 1881"),
                     key = c(1340375, 340405,1340341,1340405,1340405,1340313))

# Change these
check <- all_data[all_data$Pol_original %in% change$old,]
check$Bee_subspecies <- NA
check$Bee_rank <- "species"
check$Bee_accepted_scientific_name <- change$new[match(check$Pol_original, change$old)]
check$Bee_accepted_name <- check$Bee_species
all_data[all_data$Pol_original %in% change$old,] <- check
```


### Plantnet
```{r}
change <- data.frame(old = c("Alchemilla arvensis", "Gladiolus hortulanus", "Iris hybrida", "Phoebanthus grandiflorus", "Rubus uncinellus", "Tradescantia andersoniana"),
                     new=  c("Aphanes arvensis L.", "Gladiolus × gandavensis Van Houtte","Iris × germanica L.","Phoebanthus grandiflora (Torr. & A.Gray) S.F.Blake",
                             "Rubus acheruntinus (Ten.) Ten.", "Tradescantia virginiana L."),
                     spec = c("Aphanes arvensis", "Gladiolus gandavensis", "Iris germanica", "Phoebanthus grandiflora", "Rubus acheruntinus", "Tradescantia virginiana"),
                     key = c(5365013, 3586105,5298069, 3098664,2993408,2765272))
change$gen <- word(change$spec, 1)

# Change these
check <- all_data[all_data$Plant_plantnet %in% change$old,]
check$Plantnet_subspecies <- NA
check$Plantnet_species <- change$spec[match(check$Plant_plantnet, change$old)]
check$Plantnet_GBIF_ID <- change$key[match(check$Plant_plantnet, change$old)]
check$Plantnet_genus <- change$gen[match(check$Plant_plantnet, change$old)]
check$Plantnet_GBIF_accepted_name <- change$new[match(check$Plant_plantnet, change$old)]
check$Plant_plantnet <- change$spec[match(check$Plant_plantnet, change$old)]
all_data[all_data$Plant_plantnet %in% change$old,] <- check
```


### User
```{r}
change <- data.frame(old = c("Lamium purpureum + Lamium hybridum", "Lotus corniculatus var. corniculatus + Lotus corniculatus var. sativus", "Salix aurita + Salix cinerea",
                             "Medicago falcata + Medicago sativa"," Malva alcea + Malva moschata", "Lotus corniculatus + Lotus glaber","Calamintha spec.",
                             "Vicia sativa subsp. angustifolia + Vicia sativa subsp. segetalis","Phleum nodosum + Phleum pratense","Cardaminopsis spec.",
                             "Fragaria vesca + Fragaria moschata","Centaurea bella", "Salix udensis 'Sekka' x Salix viminalis", "Dorotheanthus spec.",
                             "Malva moschata"),
                     new = c("Lamium L.", "Lotus corniculatus L.", "Salix L.", "Medicago L.", "Malva L.", "Lotus L." , "Clinopodium L.","Vicia sativa L.", "Phleum L.",
                             "Arabidopsis Heynh.", "Fragaria L.", "Psephellus bellus (Trautv.) Wagenitz", "Salix L.", "Cleretum N.E.Br.", "Malva L."),
                     rank = c("genus", "species", "genus", "genus", "genus", "genus", "genus", "species", "genus", "genus", "genus", "species", "genus", "genus", "genus"),
                     key = c(2926678,5357013, 3039576, 2965200, 3152364,10220564 ,2926907,2975014,2706001,3052435,3029779,3137947,3039576,7329475, 3152364))
change$gen <- word(change$new, 1)
change$spec <- NA
change$spec[change$rank %in% "species"] <- word(change$new[change$rank %in% "species"], 1,2)
change$final <- change$spec
change$final[is.na(change$final)] <- change$gen[is.na(change$final)] 
  
# Change these
check <- all_data[all_data$User_original %in% change$old,]
check$User_subspecies <- NA
check$User_species <- change$spec[match(check$User_original, change$old)]
check$User_GBIF_ID <- change$key[match(check$User_original, change$old)]
check$User_genus <- change$gen[match(check$User_original, change$old)]
check$User_GBIF_accepted_name <- change$new[match(check$User_original, change$old)]
check$Plant_user <- change$final[match(check$User_original, change$old)]
check$User_rank <- change$rank[match(check$User_original, change$old)]
all_data[all_data$User_original %in% change$old,] <- check
```




## 5.6 Consensus
```{r}
# Make rank lower
all_data$User_rank <- tolower(all_data$User_rank)
all_data$Bee_rank <- tolower(all_data$Bee_rank)
all_data$Plantnet_rank <- tolower(all_data$Plantnet_rank)
all_data$User_original_rank <- tolower(all_data$User_original_rank)

# Get the final name
all_data$Plant_name <- all_data$Plant_user
all_data$Plant_rank <- all_data$User_rank
all_data$Plant_subspecies <- all_data$User_subspecies
all_data$Plant_species <- all_data$User_species
all_data$Plant_genus <- all_data$User_genus
all_data$Plant_family <- all_data$User_family
all_data$Plant_GBIF_ID <- all_data$User_GBIF_ID
all_data$Plant_GBIF_accepted_name <- all_data$User_GBIF_accepted_name
all_data$Plant_name_source <- NA
all_data$Plant_name_source[!is.na(all_data$Plant_name)] <- "User"

# The ones that are missing get the plantnet identity
all_data$Plant_name[is.na(all_data$Plant_rank)] <- all_data$Plant_plantnet[is.na(all_data$Plant_rank)] 
all_data$Plant_subspecies[is.na(all_data$Plant_rank)] <- all_data$Plantnet_subspecies[is.na(all_data$Plant_rank) ] 
all_data$Plant_species[is.na(all_data$Plant_rank)] <- all_data$Plantnet_species[is.na(all_data$Plant_rank) ] 
all_data$Plant_genus[is.na(all_data$Plant_rank)] <- all_data$Plantnet_genus[is.na(all_data$Plant_rank) ] 
all_data$Plant_family[is.na(all_data$Plant_rank)] <- all_data$Plantnet_family[is.na(all_data$Plant_rank) ] 
all_data$Plant_rank[is.na(all_data$Plant_rank)] <- all_data$Plantnet_rank[is.na(all_data$Plant_rank) ] 
all_data$Plant_GBIF_ID[is.na(all_data$Plant_GBIF_ID)] <- all_data$Plantnet_GBIF_ID[is.na(all_data$Plant_GBIF_ID) ] 
all_data$Plant_GBIF_accepted_name[is.na(all_data$Plant_GBIF_accepted_name)] <- all_data$Plantnet_GBIF_accepted_name[is.na(all_data$Plant_GBIF_accepted_name) ] 
all_data$Plant_name_source[!is.na(all_data$Plant_name) & is.na(all_data$Plant_name_source)] <- "Plantnet"
```


```{r}
# We assign plant level identification if genus is the same
# Only if it has a plantnet species or subspecies name this is relevant, otherwise it would just be the same as the user provided name
check <- all_data[is.na(all_data$Plant_species) & !is.na(all_data$Plant_genus) & !is.na(all_data$Plantnet_species),]
# If the genus is the same, we will assign the plantnet name (31995)
check <- check[check$User_genus == check$Plantnet_genus,]
# We will assign the official name, so start from subspecies level on (191)
sum(!is.na(check$Plantnet_subspecies))

# Assign to the Plantnet name
all_data$Plant_name[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plant_plantnet[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_rank[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_rank[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_subspecies[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_subspecies[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_species[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_species[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_GBIF_accepted_name[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_GBIF_accepted_name[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_GBIF_ID[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_GBIF_ID[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_name_source[all_data$Obs_ID %in% check$Obs_ID] <- "Plantnet"


# We do the same if the family levels overlap
# Here there must be at least a genus identification from plantnet
check <- all_data[is.na(all_data$Plant_species) & is.na(all_data$Plant_genus)  & !is.na(all_data$Plant_family) & !is.na(all_data$Plantnet_genus),]
# These are only 807 observations of which 643 correspond
check <- check[check$User_family == check$Plantnet_family,]
sum(!is.na(check$Plantnet_subspecies))

# Assign to the Plantnet name
all_data$Plant_name[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plant_plantnet[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_rank[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_rank[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_subspecies[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_subspecies[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_species[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_species[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_genus[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_genus[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_GBIF_accepted_name[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_GBIF_accepted_name[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_GBIF_ID[all_data$Obs_ID %in% check$Obs_ID] <- all_data$Plantnet_GBIF_ID[all_data$Obs_ID %in% check$Obs_ID]
all_data$Plant_name_source[all_data$Obs_ID %in% check$Obs_ID] <- "Plantnet"
```



## 5.7 Save
```{r}
#all_data <- read_csv( "../Results/Bees_all_observations.csv")
write_csv(all_data, "../Results/Bees_all_observations.csv")
```

